### 2024-10-14 draft.tex
added Tex file

\documentclass[11pt]{article}

\usepackage{sectsty}
\usepackage{graphicx}

% Margins
\topmargin=-0.45in
\evensidemargin=0in
\oddsidemargin=0in
\textwidth=6.5in
\textheight=9.0in
\headsep=0.25in

\title{ BareTag Tool-Tracker}
\author{ Walter Tebbetts, Sean Brown, Ken Su, and Connor McGarry }
\date{\today}

\begin{document}
\maketitle	
\pagebreak

% Optional TOC
% \tableofcontents
% \pagebreak

%--Paper--

\section{Section 1}

Lorem Impsum

\pagebreak
\section{Section 2}
Lorem Ipsum \\

%--/Paper--

\end{document}

### 2024-10-15 draft.tex
wrote abstract

@@
 \title{ BareTag Tool-Tracker}
-\author{ Walter Tebbetts, Sean Brown, Ken Su, and Connor McGarry }
-\date{\today}
+\author{ Walter Tebbetts, CompE, Sean Brown, CompE, \\ Ken Su, CompE, and Connor McGarry, CompE}
+\date{October 14, 2024}
 
@@
 
-% Optional TOC
-% \tableofcontents
-% \pagebreak
+\begin{abstract}
+    Over the past 10 years, the majority of tools on a construction 
+    site have converted from wired to battery-powered. While this 
+    makes tools easy to move around, it also makes them easy to misplace
+    and an easier target for theives. Data indicates that the construction
+    idustry suffered nearly \$1,000,000,000 in loses due to tool theft in
+    2023 alone [1], strongly indicating the need for a robust and effective 
+    theft mitigation system. We propose the BareTag Tool-Tracker, a novel
+    approach to tool tracking that utilizes Ultra-Wideband(UWB) and Bluetooth 
+    Low-Energy(BLE) radio in order to real-time track tools, materials, or other 
+    valuable items on a construction site. The system utilizes a series
+    of pre-placed Anchor posts, that send UWB pings to a Tag that is connected
+    to a tool. Each Anchor can then calculate its distance to a Tag, relaying
+    that information to a Base station over Long Range(LoRa) radio. The 
+    base station runs the aggregated distance data through a multilateration
+    algorithm that can calculate the Tag's location with $\pm$ 10 cm accuracy.
+    The calculated location is then output to a local terminal, as well as 
+    uploaded to a cloud database for future reference. Altogether, the BareTag Tool-Tracker
+    is highly accurate ($\pm$ 10 cm), low-power (1 year of battery life), and
+    scalable (increase range by adding additional Anchors).
 
-%--Paper--
+\end{abstract}
 
@@
 \section{Section 2}
-Lorem Ipsum \\
+Lorem Ipsum \\ h
 

### 2024-10-18 draft.tex
ieee template + significance

@@
-\documentclass[11pt]{article}
+\documentclass[conference]{IEEEtran}
+\IEEEoverridecommandlockouts
+% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
+\usepackage{cite}
+\usepackage{amsmath,amssymb,amsfonts}
+\usepackage{algorithmic}
+\usepackage{graphicx}
+\usepackage{textcomp}
+\usepackage{xcolor}
+\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
+    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+\begin{document}
 
-\usepackage{sectsty}
-\usepackage{graphicx}
+\title{BareTag Tool-Tracker*\\
+{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
+should not be used}
+\thanks{Identify applicable funding agency here. If none, delete this.}
+}
 
-% Margins
-\topmargin=-0.45in
-\evensidemargin=0in
-\oddsidemargin=0in
-\textwidth=6.5in
-\textheight=9.0in
-\headsep=0.25in
+\author{\IEEEauthorblockN{1\textsuperscript{st} Walter Tebbetts}
+\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+\textit{name of organization (of Aff.)}\\
+City, Country \\
+email address or ORCID}
+\and
+\IEEEauthorblockN{2\textsuperscript{nd} Sean Brown}
+\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+\textit{name of organization (of Aff.)}\\
+City, Country \\
+email address or ORCID}
+\and
+\IEEEauthorblockN{3\textsuperscript{rd} Ken Su}
+\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+\textit{name of organization (of Aff.)}\\
+City, Country \\
+email address or ORCID}
+\and
+\IEEEauthorblockN{4\textsuperscript{th} Connor McGarry}
+\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+\textit{name of organization (of Aff.)}\\
+City, Country \\
+email address or ORCID}
+\and
+\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
+\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+\textit{name of organization (of Aff.)}\\
+City, Country \\
+email address or ORCID}
+\and
+\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
+\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+\textit{name of organization (of Aff.)}\\
+City, Country \\
+email address or ORCID}
+}
 
-\title{ BareTag Tool-Tracker}
-\author{ Walter Tebbetts, CompE, Sean Brown, CompE, \\ Ken Su, CompE, and Connor McGarry, CompE}
-\date{October 14, 2024}
-
-\begin{document}
 \maketitle
-\pagebreak
 
@@
     scalable (increase range by adding additional Anchors).
-
 \end{abstract}
 
-\section{Section 1}
+\begin{IEEEkeywords}
+component, formatting, style, styling, insert
+\end{IEEEkeywords}
 
-Lorem Impsum
+\section{Introduction}
+On constructions sites tools are constantly being misplaced or passed around causing workers to spend extra time searching and waiting before returning to their assignments.
+Furthermore, in recent years research has shown that theft on constructions sites has built up costs for construction companies and slowing down projects, very detrimental for small companies.
+In recent years many different approaches have been taken to solve this growing issue.
+\subsection{Significance}
+In 2016 it was estimated that in the United States alone \$1,000,000,000 worth of construction tools were stolen [1].
+A survey by the Charted Institute of Building discovered that out of the 1000 construction mangers interviewed, a third responded that they had experienced theft weekly on their sites.
+It was estimated that each of these weekly incidents cost the business an average of \$6,000, in some cases, in a single night the site had lost \$100,000 worth of equipment [2].
+What’s worse is that this is a growing case.
+The FBI has reported that in 2021, theft on construction sites had outgrown theft in convenience stores [3].
+Many managers have reported that these incidents have escalated to organized crime with evidence of sophisticated planning and coordinated executions.
+[2].
+Theft on the site is not only costly to the business owners but also even more inconvenient for the construction workers and their managers.
+Due to the lack of proper tools construction workers may not continue with their assignments and managers have to keep pushing deadlines.
+The result of this costs the business not just in extra wages, but also extra insurance and the company’s reputation [2].
 
-\pagebreak
-\section{Section 2}
-Lorem Ipsum \\ h
+\section{Ease of Use}
 
-%--/Paper--
+\subsection{Maintaining the Integrity of the Specifications}
+
+The IEEEtran class file is used to format your paper and style the text. All margins, 
+column widths, line spaces, and text fonts are prescribed; please do not 
+alter them. You may note peculiarities. For example, the head margin
+measures proportionately more than is customary. This measurement 
+and others are deliberate, using specifications that anticipate your paper 
+as one part of the entire proceedings, and not as an independent document. 
+Please do not revise any of the current designations.
+
+\section{Prepare Your Paper Before Styling}
+Before you begin to format your paper, first write and save the content as a 
+separate text file. Complete all content and organizational editing before 
+formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
+proofreading, spelling and grammar.
+
+Keep your text and graphic files separate until after the text has been 
+formatted and styled. Do not number text heads---{\LaTeX} will do that 
+for you.
+
+\subsection{Abbreviations and Acronyms}\label{AA}
+Define abbreviations and acronyms the first time they are used in the text, 
+even after they have been defined in the abstract. Abbreviations such as 
+IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
+abbreviations in the title or heads unless they are unavoidable.
+
+\subsection{Units}
+\begin{itemize}
+\item Use either SI (MKS) or CGS as primary units.
+(SI units are encouraged.) English units may be used as secondary units (in parentheses).
+An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
+\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
+This often leads to confusion because equations do not balance dimensionally.
+If you must use mixed units, clearly state the units for each quantity that you use in an equation.
+\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
+Spell out units when they appear in text: ``.
+.
+.
+a few henries'', not ``.
+.
+.
+a few H''.
+\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
+\end{itemize}
+
+\subsection{Equations}
+Number equations consecutively. To make your 
+equations more compact, you may use the solidus (~/~), the exp function, or 
+appropriate exponents. Italicize Roman symbols for quantities and variables, 
+but not Greek symbols. Use a long dash rather than a hyphen for a minus 
+sign. Punctuate equations with commas or periods when they are part of a 
+sentence, as in:
+\begin{equation}
+a+b=\gamma\label{eq}
+\end{equation}
+
+Be sure that the 
+symbols in your equation have been defined before or immediately following 
+the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
+the beginning of a sentence: ``Equation \eqref{eq} is . . .''
+
+\subsection{\LaTeX-Specific Advice}
+
+Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
+of ``hard'' references (e.g., \verb|(1)|). That will make it possible
+to combine sections, add equations, or change the order of figures or
+citations without having to go through the file line by line.
+
+Please don't use the \verb|{eqnarray}| equation environment. Use
+\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
+environment leaves unsightly spaces around relation symbols.
+
+Please note that the \verb|{subequations}| environment in {\LaTeX}
+will increment the main equation counter even when there are no
+equation numbers displayed. If you forget that, you might write an
+article in which the equation numbers skip from (17) to (20), causing
+the copy editors to wonder if you've discovered a new method of
+counting.
+
+{\BibTeX} does not work by magic. It doesn't get the bibliographic
+data from thin air but from .bib files. If you use {\BibTeX} to produce a
+bibliography you must send the .bib files.
+
+{\LaTeX} can't read your mind. If you assign the same label to a
+subsubsection and a table, you might find that Table I has been cross
+referenced as Table IV-B3.
+
+{\LaTeX} does not have precognitive abilities. If you put a
+\verb|\label| command before the command that updates the counter it's
+supposed to be using, the label will pick up the last counter to be
+cross referenced instead. In particular, a \verb|\label| command
+should not go before the caption of a figure or a table.
+
+Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
+will not stop equation numbers inside \verb|{array}| (there won't be
+any anyway) and it might stop a wanted equation number in the
+surrounding equation.
+
+\subsection{Some Common Mistakes}\label{SCM}
+\begin{itemize}
+\item The word ``data'' is plural, not singular.
+\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
+\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
+When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
+A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
+(A parenthetical sentence is punctuated within the parentheses.)
+\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
+\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
+\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
+\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
+\item Do not confuse ``imply'' and ``infer''.
+\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
+\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
+\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
+\end{itemize}
+An excellent style manual for science writers is \cite{b7}.
+
+\subsection{Authors and Affiliations}
+\textbf{The class file is designed for, but not limited to, six authors.} A 
+minimum of one author is required for all conference articles. Author names 
+should be listed starting from left to right and then moving down to the 
+next line. This is the author sequence that will be used in future citations 
+and by indexing services. Names should not be listed in columns nor group by 
+affiliation. Please keep your affiliations as succinct as possible (for 
+example, do not differentiate among departments of the same organization).
+
+\subsection{Identify the Headings}
+Headings, or heads, are organizational devices that guide the reader through 
+your paper. There are two types: component heads and text heads.
+
+Component heads identify the different components of your paper and are not 
+topically subordinate to each other. Examples include Acknowledgments and 
+References and, for these, the correct style to use is ``Heading 5''. Use 
+``figure caption'' for your Figure captions, and ``table head'' for your 
+table title. Run-in heads, such as ``Abstract'', will require you to apply a 
+style (in this case, italic) in addition to the style provided by the drop 
+down menu to differentiate the head from the text.
+
+Text heads organize the topics on a relational, hierarchical basis. For 
+example, the paper title is the primary text head because all subsequent 
+material relates and elaborates on this one topic. If there are two or more 
+sub-topics, the next level head (uppercase Roman numerals) should be used 
+and, conversely, if there are not at least two sub-topics, then no subheads 
+should be introduced.
+
+\subsection{Figures and Tables}
+\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
+bottom of columns. Avoid placing them in the middle of columns. Large 
+figures and tables may span across both columns. Figure captions should be 
+below the figures; table heads should appear above the tables. Insert 
+figures and tables after they are cited in the text. Use the abbreviation 
+``Fig.~\ref{fig}'', even at the beginning of a sentence.
+
+\begin{table}[htbp]
+\caption{Table Type Styles}
+\begin{center}
+\begin{tabular}{|c|c|c|c|}
+\hline
+\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
+\cline{2-4} 
+\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
+\hline
+copy& More table copy$^{\mathrm{a}}$& &  \\
+\hline
+\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
+\end{tabular}
+\label{tab1}
+\end{center}
+\end{table}
+
+\begin{figure}[htbp]
+\centerline{\includegraphics{fig1.png}}
+\caption{Example of a figure caption.}
+\label{fig}
+\end{figure}
+
+Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
+rather than symbols or abbreviations when writing Figure axis labels to 
+avoid confusing the reader. As an example, write the quantity 
+``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
+units in the label, present them within parentheses. Do not label axes only 
+with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
+\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
+quantities and units. For example, write ``Temperature (K)'', not 
+``Temperature/K''.
+
+\section*{Acknowledgment}
+
+The preferred spelling of the word ``acknowledgment'' in America is without 
+an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
+G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
+acknowledgments in the unnumbered footnote on the first page.
+
+\section*{References}
+
+Please number citations consecutively within brackets \cite{b1}. The 
+sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
+number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
+the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
+
+Number footnotes separately in superscripts. Place the actual footnote at 
+the bottom of the column in which it was cited. Do not put footnotes in the 
+abstract or reference list. Use letters for table footnotes.
+
+Unless there are six authors or more give all authors' names; do not use 
+``et al.''. Papers that have not been published, even if they have been 
+submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
+that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
+Capitalize only the first word in a paper title, except for proper nouns and 
+element symbols.
+
+For papers published in translation journals, please give the English 
+citation first, followed by the original foreign-language citation \cite{b6}.
+
+\begin{thebibliography}{00}
+\bibitem{b1} G.
+Eason, B.
+Noble, and I.
+N.
+Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil.
+Trans.
+Roy.
+Soc.
+London, vol.
+A247, pp.
+529--551, April 1955.
+\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
+\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
+\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
+\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
+\bibitem{b6} Y.
+Yorozu, M.
+Hirano, K.
+Oka, and Y.
+Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl.
+J.
+Magn.
+Japan, vol.
+2, pp.
+740--741, August 1987 [Digests 9th Annual Conf.
+Magnetics Japan, p.
+301, 1982].
+\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
+\end{thebibliography}
+\vspace{12pt}
+\color{red}
+IEEE conference templates contain guidance text for composing and formatting conference papers.
+Please ensure that all template text is removed from your conference paper prior to submission to the conference.
+Failure to remove the template text from your paper may result in your paper not being published.
 

### 2024-10-19 draft.tex
{Added my latest changes into latex, did some name formatting, and added the hardware block diagram}

@@
 \documentclass[conference]{IEEEtran}
+\usepackage{graphicx}
 \IEEEoverridecommandlockouts
@@
 
-\title{BareTag Tool-Tracker*\\
-{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
-should not be used}
-\thanks{Identify applicable funding agency here. If none, delete this.}
+\title{BareTag Tool-Tracker\\
+{\footnotesize {Team 3 - University of Massachusetts Amherst Senior Design Project 2025 }}
 }
 
-\author{\IEEEauthorblockN{1\textsuperscript{st} Walter Tebbetts}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
+\author{
+    \IEEEauthorblockN{Sean Brown}
+    \IEEEauthorblockA{\textit{Computer Engineering} \\
+    \textit{Logistics Lead}\\}
     \and
-\IEEEauthorblockN{2\textsuperscript{nd} Sean Brown}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
+    \IEEEauthorblockN{Connor McGarry}
+    \IEEEauthorblockA{\textit{Computer Engineering} \\
+    \textit{Hardware Lead}\\}
     \and
-\IEEEauthorblockN{3\textsuperscript{rd} Ken Su}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
+    \IEEEauthorblockN{Ken Su}
+    \IEEEauthorblockA{\textit{Computer Engineering} \\
+    \textit{Budget Lead}\\}
     \and
-\IEEEauthorblockN{4\textsuperscript{th} Connor McGarry}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
+    \IEEEauthorblockN{Walter Tebbetts}
+    \IEEEauthorblockA{\textit{Computer Engineering} \\
+    \textit{Software Lead}\\}
     \and
-\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
-\and
-\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
+    \IEEEauthorblockN{Professor Jeremy Gummeson}
+    \IEEEauthorblockA{\textit{UMass Amherst ECE Faculty} \\
+    \textit{Advisor}\\}
 }
@@
 
-\section{Ease of Use}
+\section{DESIGN}
 
-\subsection{Maintaining the Integrity of the Specifications}
+This section describes the system design including design alternatives, design justifications, and hardware and software block diagrams.
 
-The IEEEtran class file is used to format your paper and style the text. All margins, 
-column widths, line spaces, and text fonts are prescribed; please do not 
-alter them. You may note peculiarities. For example, the head margin
-measures proportionately more than is customary. This measurement 
-and others are deliberate, using specifications that anticipate your paper 
-as one part of the entire proceedings, and not as an independent document. 
-Please do not revise any of the current designations.
+\section{Overview}
+At a high level, the BareTag Tool Tracker utilizes Ultra-Wideband (UWB), Bluetooth Low Energy (BLE), and LoRa radio in order to real-time track an item's location on a construction site.
+The technology at the core of our design is UWB radio.
+UWB radio is a form of radio communication that utilizes pulses of radio energy at specifically timed intervals in order to transmit information.
+This protocol is not ideal for data communication, but is very accurate in performing distance ranging.
+With two UWB transceivers, one configured as the controller (Anchor) and the other configured as the responder (Tag), the controller can send a UWB ping to the responder.
+The responder will almost immediately send back a response ping, the controller can then use the time between when it sent its ping to when it received the response ping, in order to calculate the distance between the two transceivers.
 
-\section{Prepare Your Paper Before Styling}
-Before you begin to format your paper, first write and save the content as a 
-separate text file. Complete all content and organizational editing before 
-formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
-proofreading, spelling and grammar.
+\begin{figure}
+\includegraphics[scale=0.185]{Screenshot from 2024-10-18 21-37-02.png}
+\caption{Full system hardware block diagram}
+\end{figure}
 
-Keep your text and graphic files separate until after the text has been 
-formatted and styled. Do not number text heads---{\LaTeX} will do that 
-for you.
+\subsection{Tag}\label{AA}
+The Tag refers to the trackable device that will be attached to the tools on a worksite.
+The goal is for the Tags to be less than 31.9mm2, which is of a similar size to the Apple Airtag.
+The thickness of the Tags is aimed to be under 16mm, with the primary contributor to this size being the pouch cell 290mAh Lithium Polymer battery.
+The peak current draw of the Tag is 45mA and is out of the range that a coin cell could support, which led to the decision to use a LiPo that fits within our area size goals at 25 mm x 28mm.
+We are aiming for a one year battery life.
+The primary part of the Tag is the Qorvo DWM3001C.
+This module is driven by the nRF52833 MCU, and includes BLE, UWB, and accelerometer functionality.
+The DWM3001 provides UWB functionality and has an integrated PCB antenna which requires a keep-out zone in the Tag.
+BLE is provided by the nRF52833.
+This MCU is built on an ARM Cortex M4 and operates in the 2.4GHz band.
+This MCU is programmable over JTAG and thus requires a JTAG interface to be added to the Tag PCBs.
+The accelerometer is the LIS12DH, and is used to wake up the module upon motion detection.
+The module will set the interrupt pin on the DWM3001 high when there is motion detected.
+Otherwise, the Tag is in a low power mode to save battery life and is not receiving UWB pings.
+Therefore, before the tag goes to sleep the location needs to be checked to determine the resting location.
+The Tag has the BLE radio turned off until it exits the UWB perimeter, at which point an interrupt pin turns it on to integrate into the Apple Find My network.
+At this point, the UWB module turns off to conserve power.
+The accelerometer still regulates the power mode of the Tag depending on motion to conserve power.
+This device draws a lot of concepts from ECE 523 and ECE 304, both of which have a heavy focus on minimizing power consumption via software and component selection.
+The TPS79933 voltage regulator has an output of 3.3V when the input voltage is over 3.475V.
+This component is used in both the Tags and Anchors as both devices operate on a 3.7V input battery with 3.3V ideal operating voltage.
 
-\subsection{Abbreviations and Acronyms}\label{AA}
-Define abbreviations and acronyms the first time they are used in the text, 
-even after they have been defined in the abstract. Abbreviations such as 
-IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
-abbreviations in the title or heads unless they are unavoidable.
+\subsection{Anchor}
+There needs to exist at least 3 anchors for the coordinates to be transmitted to the user.
+This is performed through multilateration.
+The Anchors use the same Qorvo DWM3001C modules as on the Tags as all of the submodules have a use case here too.
+The Anchors use UWB to ping the Tag and determine its location within the area defined by the proximity of the other anchors.
+They operate on this data using the nRF52833 MCU and send it to a host device over LoRaWAN.
+The RYLR998 LoRa module in the Anchors operates within the required range for LoRaWAN of 902.3 to 914.9 MHz.
+This module communicates with the MCU via UART.
+The use of these LoRa modules means that the Host Device does not need to be exactly on the site of the construction due to the kilometers of range that LoRa supports.
+We will build the LoRaWAN protocol on top of LoRa using the nRF52833 MCU.
+The use of this MCU also means that we can take advantage of the BLE it provides and use it for a variety of functions.
+The GPS coordinates of the Anchors must be known in order to get the real-world position of the Tags.
+We can also use BLE to communicate with an anchor to alert that a Tag that is in BLE mode has been returned to the UWB-supported area.
+These features result in  more power consumption than the Tags, so a 2.2Ah Lithium Ion battery is used.
+This is possible due to less size constraints for the Anchors than of the Tag.
+The size of the Anchor is not a specification that matters, however they will be able to be mounted on posts or stuck in different site locations depending on the desired use and area to cover.
+As stated before, the TPS79933 voltage regulator outputs 3.3V, which is the ideal operating voltage for the DWM3001C, along with the LoRa module.
 
-\subsection{Units}
-\begin{itemize}
-\item Use either SI (MKS) or CGS as primary units.
-(SI units are encouraged.) English units may be used as secondary units (in parentheses).
-An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
-\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
-This often leads to confusion because equations do not balance dimensionally.
-If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
-Spell out units when they appear in text: ``.
-.
-.
-a few henries'', not ``.
-.
-.
-a few H''.
-\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
-\end{itemize}
+\subsection{Lora Dongle}
+This device is a RYLR998 operating over a USB - UART connection with the Host Device.
+It allows for the Host Device to receive the Tag coordinate data and operate on it.
+The size of this device should account for the LoRa module plus a USB/UART converter (CP2102N).
+The size should be similar to that of a USB hub, as to not be an inconvenience to have attached to a small host device.
+As such, the dimensions should be approximately 32 x 18 x 8 mm based on a combination of the component dimensions.
+The Dongle receives power from the CP2102N over a wired USB-C connection, so there is no need for an external power supply.
 
-\subsection{Equations}
-Number equations consecutively. To make your 
-equations more compact, you may use the solidus (~/~), the exp function, or 
-appropriate exponents. Italicize Roman symbols for quantities and variables, 
-but not Greek symbols. Use a long dash rather than a hyphen for a minus 
-sign. Punctuate equations with commas or periods when they are part of a 
-sentence, as in:
-\begin{equation}
-a+b=\gamma\label{eq}
-\end{equation}
+\subsection{Host Device}
 
-Be sure that the 
-symbols in your equation have been defined before or immediately following 
-the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
-the beginning of a sentence: ``Equation \eqref{eq} is . . .''
-
-\subsection{\LaTeX-Specific Advice}
-
-Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
-of ``hard'' references (e.g., \verb|(1)|). That will make it possible
-to combine sections, add equations, or change the order of figures or
-citations without having to go through the file line by line.
-
-Please don't use the \verb|{eqnarray}| equation environment. Use
-\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
-environment leaves unsightly spaces around relation symbols.
-
-Please note that the \verb|{subequations}| environment in {\LaTeX}
-will increment the main equation counter even when there are no
-equation numbers displayed. If you forget that, you might write an
-article in which the equation numbers skip from (17) to (20), causing
-the copy editors to wonder if you've discovered a new method of
-counting.
-
-{\BibTeX} does not work by magic. It doesn't get the bibliographic
-data from thin air but from .bib files. If you use {\BibTeX} to produce a
-bibliography you must send the .bib files.
-
-{\LaTeX} can't read your mind. If you assign the same label to a
-subsubsection and a table, you might find that Table I has been cross
-referenced as Table IV-B3.
-
-{\LaTeX} does not have precognitive abilities. If you put a
-\verb|\label| command before the command that updates the counter it's
-supposed to be using, the label will pick up the last counter to be
-cross referenced instead. In particular, a \verb|\label| command
-should not go before the caption of a figure or a table.
-
-Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
-will not stop equation numbers inside \verb|{array}| (there won't be
-any anyway) and it might stop a wanted equation number in the
-surrounding equation.
+This device can be whatever system a supervisor desires to use as long as it can support a physical USB/Serial connection, or do so using adapters.
+The Host Device is backhauling the location data of each Tag to a database where the history of the tag locations can be mapped out to determine the daily path.
+This information is also displayed in real time on a map of the desired area.
+The Host Device is also running the macless-haystack Find My server, which acts as a means for tracking the Tags that have left the UWB area and are now using BLE to integrate with the Apple Find My network.
+The tags all have unique IDs that can be linked to tools or equipment, making it easy to parse the data and determine what items have been in what location.
 
@@
 \begin{figure}[htbp]
-\centerline{\includegraphics{fig1.png}}
 \caption{Example of a figure caption.}

### 2024-10-19 draft.tex
clarified subsections

--- 2024-10-15 draft.tex
@@
-\documentclass[11pt]{article}
+\documentclass[conference]{IEEEtran}
+\IEEEoverridecommandlockouts
+% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
+\usepackage{cite}
+\usepackage{amsmath,amssymb,amsfonts}
+\usepackage{algorithmic}
+\usepackage{graphicx}
+\usepackage{textcomp}
+\usepackage{xcolor}
+\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
+    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+\begin{document}
 
-\usepackage{sectsty}
-\usepackage{graphicx}
+\title{BareTag Tool-Tracker*\\
+{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
+should not be used}
+\thanks{Identify applicable funding agency here. If none, delete this.}
+}
 
-% Margins
-\topmargin=-0.45in
-\evensidemargin=0in
-\oddsidemargin=0in
-\textwidth=6.5in
-\textheight=9.0in
-\headsep=0.25in
+\author{\IEEEauthorblockN{Walter Tebbetts}
+\textit{CompE}\\
+\textit{Software Lead}
 
-\title{ BareTag Tool-Tracker}
-\author{ Walter Tebbetts, CompE, Sean Brown, CompE, \\ Ken Su, CompE, and Connor McGarry, CompE}
-\date{October 14, 2024}
+\and
+\IEEEauthorblockN{Sean Brown}
+\textit{CompE}\\
+\textit{Logistics Lead}
 
-\begin{document}
+\and
+\IEEEauthorblockN{Ken Su}
+\textit{CompE}\\
+\textit{Budget Lead}
+
+\and
+\IEEEauthorblockN{Connor McGarry}
+\textit{CompE}\\
+\textit{Hardware Lead}
+
+}
+
 \maketitle
-\pagebreak
 
@@
     scalable (increase range by adding additional Anchors).
-
 \end{abstract}
 
-\section{Section 1}
+\begin{IEEEkeywords}
+component, formatting, style, styling, insert
+\end{IEEEkeywords}
 
-Lorem Impsum
+\section{Introduction}
+On constructions sites tools are constantly being misplaced or passed around causing workers to spend extra time searching and waiting before returning to their assignments.
+Furthermore, in recent years research has shown that theft on constructions sites has built up costs for construction companies and slowing down projects, very detrimental for small companies.
+In recent years many different approaches have been taken to solve this growing issue.
+\subsection{Significance}
+In 2016 it was estimated that in the United States alone \$1,000,000,000 worth of construction tools were stolen [1].
+A survey by the Charted Institute of Building discovered that out of the 1000 construction mangers interviewed, a third responded that they had experienced theft weekly on their sites.
+It was estimated that each of these weekly incidents cost the business an average of \$6,000, in some cases, in a single night the site had lost \$100,000 worth of equipment [2].
+What’s worse is that this is a growing case.
+The FBI has reported that in 2021, theft on construction sites had outgrown theft in convenience stores [3].
+Many managers have reported that these incidents have escalated to organized crime with evidence of sophisticated planning and coordinated executions.
+[2].
+Theft on the site is not only costly to the business owners but also even more inconvenient for the construction workers and their managers.
+Due to the lack of proper tools construction workers may not continue with their assignments and managers have to keep pushing deadlines.
+The result of this costs the business not just in extra wages, but also extra insurance and the company’s reputation [2].
 
-\pagebreak
-\section{Section 2}
-Lorem Ipsum \\ h
+\subsection{Context and Survey of Similar Solutions}
 
-%--/Paper--
+The IEEEtran class file is used to format your paper and style the text. All margins, 
+column widths, line spaces, and text fonts are prescribed; please do not 
+alter them. You may note peculiarities. For example, the head margin
+measures proportionately more than is customary. This measurement 
+and others are deliberate, using specifications that anticipate your paper 
+as one part of the entire proceedings, and not as an independent document. 
+Please do not revise any of the current designations.
+
+\subsection{Societal Impacts}
+Define abbreviations and acronyms the first time they are used in the text, 
+even after they have been defined in the abstract. Abbreviations such as 
+IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
+abbreviations in the title or heads unless they are unavoidable.
+
+\subsection{Goals Specifications and Testing Plan}
+\begin{itemize}
+\item Use either SI (MKS) or CGS as primary units.
+(SI units are encouraged.) English units may be used as secondary units (in parentheses).
+An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
+\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
+This often leads to confusion because equations do not balance dimensionally.
+If you must use mixed units, clearly state the units for each quantity that you use in an equation.
+\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
+Spell out units when they appear in text: ``.
+.
+.
+a few henries'', not ``.
+.
+.
+a few H''.
+\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
+\end{itemize}
+
+\section{Design}
+
+\subsection{Overview}
+At a high level, the BareTag Tool Tracker utilizes Ultra-Wideband (UWB), 
+Bluetooth Low Energy (BLE), and LoRa radio in order to real-time track an 
+item's location on a construction site. The technology at the core of our 
+design is UWB radio. UWB radio is a form of radio communication that 
+utilizes pulses of radio energy at specifically timed intervals in order 
+to transmit information. This protocol is not ideal for data communication, 
+but is very accurate in performing distance ranging. With two UWB 
+transceivers, one configured as the controller (Anchor) and the other 
+configured as the responder (Tag), the controller can send a UWB ping to 
+the responder. The responder will almost immediately send back a response 
+ping, the controller can then use the time between when it sent its ping to 
+when it received the response ping, in order to calculate the distance 
+between the two transceivers.
+
+\[ d = \frac{\frac{ToF}{2}}{c} \]
+Where $d$ is distance, $ToF$ is time of flight, and $c$ is the speed of light.
+
+\subsection{Tag}
+
+\subsection{Block 2}
+
+\subsection{Block 3}
+
+\subsection{Block 4}
+
+\section*{Acknowledgment}
+
+The preferred spelling of the word ``acknowledgment'' in America is without 
+an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
+G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
+acknowledgments in the unnumbered footnote on the first page.
+
+\section*{References}
+
+Please number citations consecutively within brackets \cite{b1}. The 
+sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
+number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
+the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
+
+Number footnotes separately in superscripts. Place the actual footnote at 
+the bottom of the column in which it was cited. Do not put footnotes in the 
+abstract or reference list. Use letters for table footnotes.
+
+Unless there are six authors or more give all authors' names; do not use 
+``et al.''. Papers that have not been published, even if they have been 
+submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
+that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
+Capitalize only the first word in a paper title, except for proper nouns and 
+element symbols.
+
+For papers published in translation journals, please give the English 
+citation first, followed by the original foreign-language citation \cite{b6}.
+
+\begin{thebibliography}{00}
+\bibitem{b1} G.
+Eason, B.
+Noble, and I.
+N.
+Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil.
+Trans.
+Roy.
+Soc.
+London, vol.
+A247, pp.
+529--551, April 1955.
+\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
+\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
+\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
+\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
+\bibitem{b6} Y.
+Yorozu, M.
+Hirano, K.
+Oka, and Y.
+Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl.
+J.
+Magn.
+Japan, vol.
+2, pp.
+740--741, August 1987 [Digests 9th Annual Conf.
+Magnetics Japan, p.
+301, 1982].
+\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
+\end{thebibliography}
+\vspace{12pt}
+\color{red}
+IEEE conference templates contain guidance text for composing and formatting conference papers.
+Please ensure that all template text is removed from your conference paper prior to submission to the conference.
+Failure to remove the template text from your paper may result in your paper not being published.
 

### 2024-10-19 draft.tex

--- 2024-10-19 draft.tex
@@
 
-\author{
+\author{\IEEEauthorblockN{Walter Tebbetts}
+\textit{CompE}\\
+\textit{Software Lead}
+
+\and
 \IEEEauthorblockN{Sean Brown}
-    \IEEEauthorblockA{\textit{Computer Engineering} \\
-    \textit{Logistics Lead}\\}
+\textit{CompE}\\
+\textit{Logistics Lead}
+
+\and
+\IEEEauthorblockN{Ken Su}
+\textit{CompE}\\
+\textit{Budget Lead}
+
 \and
 \IEEEauthorblockN{Connor McGarry}
-    \IEEEauthorblockA{\textit{Computer Engineering} \\
-    \textit{Hardware Lead}\\}
-    \and
-    \IEEEauthorblockN{Ken Su}
-    \IEEEauthorblockA{\textit{Computer Engineering} \\
-    \textit{Budget Lead}\\}
-    \and
-    \IEEEauthorblockN{Walter Tebbetts}
-    \IEEEauthorblockA{\textit{Computer Engineering} \\
-    \textit{Software Lead}\\}
-    \and
-    \IEEEauthorblockN{Professor Jeremy Gummeson}
-    \IEEEauthorblockA{\textit{UMass Amherst ECE Faculty} \\
-    \textit{Advisor}\\}
+\textit{CompE}\\
+\textit{Hardware Lead}
+
 }
@@
 
-\begin{table}[htbp]
-\caption{Table Type Styles}
-\begin{center}
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-\cline{2-4} 
-\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
-\hline
-copy& More table copy$^{\mathrm{a}}$& &  \\
-\hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
-\end{tabular}
-\label{tab1}
-\end{center}
-\end{table}
+\[ d = \frac{\frac{ToF}{2}}{c} \]
+Where $d$ is distance, $ToF$ is time of flight, and $c$ is the speed of light.
 
-\begin{figure}[htbp]
-\caption{Example of a figure caption.}
-\label{fig}
-\end{figure}
+\subsection{Tag}
 
-Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
-rather than symbols or abbreviations when writing Figure axis labels to 
-avoid confusing the reader. As an example, write the quantity 
-``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
-units in the label, present them within parentheses. Do not label axes only 
-with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
-\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
-quantities and units. For example, write ``Temperature (K)'', not 
-``Temperature/K''.
+\subsection{Block 2}
+
+\subsection{Block 3}
+
+\subsection{Block 4}
 

### 2024-10-20 draft.tex
finished design overview, and reformatted

@@
 \section{Introduction}
-On constructions sites tools are constantly being misplaced or passed around causing workers to spend extra time searching and waiting before returning to their assignments.
-Furthermore, in recent years research has shown that theft on constructions sites has built up costs for construction companies and slowing down projects, very detrimental for small companies.
-In recent years many different approaches have been taken to solve this growing issue.
+On constructions sites tools are constantly being misplaced or passed 
+around causing workers to spend extra time searching and waiting before 
+returning to their assignments. Furthermore, in recent years research has 
+shown that theft on constructions sites has built up costs for construction 
+companies and slowing down projects, very detrimental for small companies. 
+In recent years many different approaches have been taken to solve this 
+growing issue.
+
 \subsection{Significance}
-In 2016 it was estimated that in the United States alone \$1,000,000,000 worth of construction tools were stolen [1].
-A survey by the Charted Institute of Building discovered that out of the 1000 construction mangers interviewed, a third responded that they had experienced theft weekly on their sites.
-It was estimated that each of these weekly incidents cost the business an average of \$6,000, in some cases, in a single night the site had lost \$100,000 worth of equipment [2].
-What’s worse is that this is a growing case.
-The FBI has reported that in 2021, theft on construction sites had outgrown theft in convenience stores [3].
-Many managers have reported that these incidents have escalated to organized crime with evidence of sophisticated planning and coordinated executions.
-[2].
-Theft on the site is not only costly to the business owners but also even more inconvenient for the construction workers and their managers.
-Due to the lack of proper tools construction workers may not continue with their assignments and managers have to keep pushing deadlines.
-The result of this costs the business not just in extra wages, but also extra insurance and the company’s reputation [2].
+
+In 2016 it was estimated that in the United States alone \$1,000,000,000 
+worth of construction tools were stolen [1]. A survey by the Charted 
+Institute of Building discovered that out of the 1000 construction mangers 
+interviewed, a third responded that they had experienced theft weekly on 
+their sites. It was estimated that each of these weekly incidents cost the 
+business an average of \$6,000, in some cases, in a single night the site 
+had lost \$100,000 worth of equipment [2]. What’s worse is that this is a 
+growing case. The FBI has reported that in 2021, theft on construction 
+sites had outgrown theft in convenience stores [3]. Many managers have 
+reported that these incidents have escalated to organized crime with 
+evidence of sophisticated planning and coordinated executions. [2]. 
+Theft on the site is not only costly to the business owners but also 
+even more inconvenient for the construction workers and their managers. 
+Due to the lack of proper tools construction workers may not continue with
+their assignments and managers have to keep pushing deadlines. The 
+result of this costs the business not just in extra wages, but also 
+extra insurance and the company’s reputation [2].
+
+\subsection{Context and Survey of Similar Solutions}
+
+The general problem of item tracking has had many attempted solutions 
+and continues to be a problem of interest today. In designing our system, 
+we extensively researched many similar solutions to examine how these 
+solutions fall short of achieving our system’s goals. Other solutions 
+we have examined use various technology for tracking such as: AI image 
+processing, GPS, Bluetooth, and Ultra-wideband.
+
+One comparable solution that utilizes image processing methods is offered 
+by SIRIX. Their approach involves human and AI-assisted item tracking, 
+using two types of cameras: wide-angle and thermal. These cameras are 
+strategically placed throughout the job site and are monitored 24/7 by both
+human operators and AI [4]. However, this solution is highly unreliable 
+and unsustainable due to the presence of blind spots that fall outside 
+the cameras' field of view, leaving certain areas unprotected. 
+Additionally, human judgments and AI decision-making can introduce 
+further response time, potentially allowing thieves to escape with 
+stolen items before any alert is triggered. Another concerning issue 
+is with the way that the system is powered. Attackers, especially a 
+criminal organization as mentioned in the problem statement could easily 
+disable the system by cutting the power generator or energy source, 
+rendering it inoperative, leaving the remote surveillance team with no 
+recourse other than calling the authorities. While both SIRIX and 
+BareTag offer 24/7 security systems, only BareTag qualifies as a 
+true round-the-clock security measure. BareTag does not depend on 
+human or AI intervention to ensure tools and materials are secure. 
+Additionally, BareTag's low power consumption allows it to operate 
+more efficiently across diverse terrains, offering higher portability 
+and flexibility compared to the energy-intensive SIRIX system.
+
+Another comparable solution we evaluated is a commercial system called 
+GoCodes, which specifically addresses the issue of tool tracking. This 
+system employs continuous GPS tracking to monitor valuable equipment 
+within a geofence, helping businesses prevent the loss or theft of tools. 
+While it offers effective on-site tracking, off-site tracking relies on 
+individuals scanning QR codes placed on the tools. If a user scans the 
+QR code, the item's location outside of the geofence can be updated [5]. 
+However, this approach has a significant flaw — no tool thief would 
+voluntarily scan the QR code, and they could easily remove the codes 
+from the tools, eliminating any trace of the theft. Although GoCodes 
+provides a workable solution, it has several drawbacks that our system 
+aims to overcome. For one, GPS tracking is power-intensive, often requiring
+frequent battery replacements for the trackers. Additionally, GPS 
+tracking needs an unobstructed line-of-sight to function efficiently, 
+which can be compromised in dynamic construction environments. 
+Furthermore, our system is designed to operate in very rural construction 
+areas where satellite connectivity may be limited. Unlike GPS, which 
+requires a strong satellite connection for accurate tracking, 
+ultra-wideband (UWB) technology, which our system uses, does not rely on 
+satellites, making it more reliable in such environments.
+
+A common solution and a more reliable approach is using the Apple AirTags.
+In the Apple AirTags, there are BLE modules that help it communicate 
+with other iPhones to create the Find My network. Additionally, it has 
+UWB modules that allow the user to get a more accurate location of where 
+the tag is once the AirTag is close enough to the user’s iPhone [6]. This 
+creates a well-rounded system to let users get a general idea of where 
+their items are with a battery life of up to a year. The difference 
+between the BareTag and the AirTag is that the BareTag is used for 
+accurately tracking high-value items within the set UWB perimeter. 
+BareTag emphasizes the use of the UWB module so construction workers 
+can easily find their tools, along with an additional BLE module for 
+the Find My Network feature outside of the set perimeter. Unlike Airtag, 
+our system aims to not only track and retrieve items but also to accurately 
+and reliability track tools to optimize efficiency.
+
+The final solution takes a similar approach to BareTag. Pozyx tracks 
+items indoors by installing UWB anchors throughout the building, which 
+communicate with UWB tags. These anchors are height-adjustable and 
+plugged into walls. Once configured and registered in the system, 
+items can be geofenced, and the collected data can be used to optimize 
+workflow and labor efficiency [7]. While Pozyx offers an effective 
+indoor tracking solution, it is less efficient in outdoor environments. 
+In locations like construction sites, where power availability may be 
+limited, anchor placement becomes a significant challenge. Additionally, 
+even though Pozyx’s UWB tags are advertised to have a battery life of over 
+five years, they are bulky and lack a low-power option. In contrast, 
+BareTag’s anchors come with pre-installed communication systems and 
+built-in batteries, making the system more portable and scalable. 
+Furthermore, BareTag’s tags feature a built-in accelerometer with an 
+automatic sleep function to maximize power efficiency. This not only 
+extends battery life but also reduces the frequency of battery 
+replacements, saving time and resources. In summary, BareTag's anchors 
+do not rely on external power sources, and the tags are equipped with a 
+low-power solution, making them more suitable for outdoor and construction 
+site use compared to Pozyx’s solution.
+
+\subsection{Societal Impacts}
+
+Our system can positively benefit all of society. As a tool tracking 
+system made for construction workers, they are the most obvious group 
+of people who benefit from this system. With construction workers being 
+the primary users of our system, many of our design choices will be made 
+specifically for the system to be easily used by the average construction 
+worker. We want to create a user-interface that helps construction workers 
+track their tools without having to do any additional work of their own. 
+While this will greatly help construction workers find their tools and 
+not have to worry about their tools being stolen, it benefits owners of 
+construction firms even more. With accurate tool tracking, they can 
+ensure their workers are working as efficiently as possible and not 
+wasting their time looking around sites for tools. Owners of construction 
+companies are also the ones responsible for supplying their workers with 
+the tools needed to complete jobs. We want our system to reduce these 
+costs for construction firm owners by reducing the loss and theft of 
+their very expensive tools. Preventing theft and increasing the 
+efficiency of workers can help a construction firm look more professional 
+and hireable by employers that need construction work done. Our system 
+aims to help construction teams work quicker to efficiently finish jobs 
+which will increase the number of jobs they can take. Because our system 
+increases construction efficiency, anyone benefiting from the construction 
+of literally anything can benefit from it as well. The only people that 
+will be hurt by our system are thieves that will be caught stealing 
+expensive tools by our system.
+
+\subsection{Goals, Specifications and Testing Plan}
+
+The BareTag Tool Tracker will implement the following goals, 1. Real-time 
+tracking within a specified zone, 2. Precise accuracy for tracking within 
+the zone, 3. Low Power,  4. Reliability outside the zone, 5. Scalability.
+
+The specifications listed in Table 1 demonstrate the goals that our project 
+aims to achieve by the time that we have a finalized product.
+\begin{center}
+\begin{table}
+\caption{Design Goals and Testing Plan}
+\begin{tabular}{|p{4cm}|p{4cm}|}
+    \hline
+    \textbf{Specification}  & \textbf{Testing Plan}\\
+    \hline
+    The system will track an item’s geo-coordinates with a reliability of 
+    95\% within a specified 100 m x 100 m zone. 
+    &
+    Ping the Tag at randomized coordinates within the Sustainable 
+    Engineering construction site.\\
+    \hline
+    The system will have less than 50 cm precision for tracking within 
+    the specified zone.
+    &
+    Compare Tag’s measured location to its actual location 
+    within a predefined grid.\\
+    \hline
+    The system will operate 24/7 for ~1 year without 
+    replacing the batteries.
+    &
+    Measure the power consumption of the system in multiple modes.\\
+    \hline
+    Ensure that the Tag can be tracked via the Find My network outside 
+    of the UWB zone.
+    &
+    Confirm tracking accuracy in scenarios with different saturations 
+    of Find My devices by comparing with AirTags in the same location.\\
+    \hline
+    Should easily be scalable to increase the range of the UWB perimeter 
+    by adding more Anchors at desired locations.
+    &
+    Demonstrate that a Tag’s trackable range in the UWB zone increases 
+    when adding a new Anchor.\\
+    \hline
+\end{tabular}
+\end{table}
+\end{center}
 
@@
 
-This section describes the system design including design alternatives, design justifications, and hardware and software block diagrams.
+This section describes the system design including design alternatives, 
+design justifications, and hardware and software block diagrams.
 
-\section{Overview}
-At a high level, the BareTag Tool Tracker utilizes Ultra-Wideband (UWB), Bluetooth Low Energy (BLE), and LoRa radio in order to real-time track an item's location on a construction site.
-The technology at the core of our design is UWB radio.
-UWB radio is a form of radio communication that utilizes pulses of radio energy at specifically timed intervals in order to transmit information.
-This protocol is not ideal for data communication, but is very accurate in performing distance ranging.
-With two UWB transceivers, one configured as the controller (Anchor) and the other configured as the responder (Tag), the controller can send a UWB ping to the responder.
-The responder will almost immediately send back a response ping, the controller can then use the time between when it sent its ping to when it received the response ping, in order to calculate the distance between the two transceivers.
+\subsection{Overview}
+At a high level, the BareTag Tool Tracker utilizes Ultra-Wideband (UWB) and 
+Bluetooth Low Energy (BLE) radio in order to real-time track an 
+item's location on a construction site. The technology at the core of our 
+design is UWB radio. UWB radio is a form of radio communication that 
+utilizes pulses of radio energy at specifically timed intervals in order 
+to transmit information. This protocol is not ideal for data communication, 
+but is very accurate in performing distance ranging. With two UWB 
+transceivers, one configured as the controller (Anchor) and the other 
+configured as the responder (Tag), the Anchor can range it's distance
+to the Tag via UWB pings. The Anchor begins by sending a ping with 
+the desired Tag's ID encoded, the Tag will almost immediately send 
+back a response ping, the Anchor can then use the time between when it 
+sent its ping to when it received the Tag's ping, in order to 
+calculate the distance between the two transceivers.
+
+\[ d = \frac{\frac{ToF}{2}}{c} \]
+
+Where $d$ is distance between the Anchor and Tag, 
+$ToF$ is time of flight, and $c$ is the speed of light.
+
+With distance measurements between 3 Anchors and 1 Tag, we
+can preform a trilateration algorithm in order to calculate
+the Tag's location within our site.
+
+The equations for the three circles (Anchor to Tag distance):
+
+\[(x - x_1)^2 + (y - y_1)^2 = r_1^2\]
+\[(x - x_2)^2 + (y - y_2)^2 = r_2^2\]
+\[(x - x_3)^2 + (y - y_3)^2 = r_3^2\]
+
+Where $r_i$ is the distance from an Anchor to a Tag, $(x_i, y_i)$ are 
+the cordinates for each Anchor on a 2D $x,y$ plane, and $(x,y)$ are the coordinates
+for the Tag we are trying to locate.\\
+Next we subtract the second equation from the first:
+
+\[(-2x_1 + 2x_2)x + (-2y_1 + 2y_2)y = r_1^2 - r_2^2 - x_1^2 + x_2^2 - y_1^2 + y_2^2\]
+
+Likewise, subtract the third equation from the second:
+\[(-2x_2 + 2x_3)x + (-2y_2 + 2y_3)y = r_2^2 - r_3^2 - x_2^2 + x_3^2 - y_2^2 + y_3^2\]
+
+Re-writing these two equations using A, B, C, D, E, and F:
+\[Ax + By = C\]
+\[Dx + Ey = F\]
+
+Finally, the Tag's $(x,y)$ coordinates are:
+\[x = \frac{CE - FB}{EA - BD}\]
+\[y = \frac{CD - AF}{BD - AE}\]
+
+Once the Tag's location has been calculated via our trilateration algorithm,
+the Tag's location will be output to a local terminal, as well as 
+uploaded to a cloud database. Outputting to a local terminal allows us to
+have the system function without the need for an internet connection, 
+something that may not be available on rural construction sites. If internet
+is available, we can upload location to cloud database. With location data
+stored remotely, any user with internet access can get their Tag's current
+location, or past location.
+
+Aditionally, as one of our main goals is to prevent theft, when a Tag
+leaves the designated construction site, a notification will be sent to 
+the user, letting them know that one of their Tag's has left the site.
+To continue to track the Tag once it leaves the construction site, we will
+turn off the Tag's UWB radio, and turn on the Tag's BLE radio. Using BLE
+advertisements, the Tag will be able to communicate with nearby devices that
+are using the Apple Find My protocol. The Find My protocol allows BLE devices
+to be tracked with around 10 meter accuracy when in loactions saturated with 
+Apple devices. With this tracking outside of the construction site, users 
+can not only keep track of their tools on a construction site, but also track
+down stolen tools outside of the construction site. To help integrate our
+Tags into the Find My network, we will be using the open source project,
+openhaystack.
+
+Openhaystack, is an open source project originating from TU Darmstadt, that
+utilizes Find My's open API, as well as a collection of reverse engineering
+and security analysis work to allow generic BLE devices to be tracked via
+Apple's Find My network.
+
+Altogether, the BareTag Tool Tracker utilizes UWB and BLE in order to real
+time track the location of Tags on and off a construction site. The design
+combines existing solutions for item tracking with UWB as well as the robust
+and expansive Find My network to prevent tool theft and increase construction
+site efficiency.
 
@@
 
-\subsection{Some Common Mistakes}\label{SCM}
-\begin{itemize}
-\item The word ``data'' is plural, not singular.
-\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
-\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
-\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
-\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
-\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
-\item Do not confuse ``imply'' and ``infer''.
-\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
-\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
-\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
-\end{itemize}
-An excellent style manual for science writers is \cite{b7}.
-
 \subsection{Authors and Affiliations}
@@
 ``Fig.~\ref{fig}'', even at the beginning of a sentence.
-
-\[ d = \frac{\frac{ToF}{2}}{c} \]
-Where $d$ is distance, $ToF$ is time of flight, and $c$ is the speed of light.
-
-\subsection{Tag}
-
-\subsection{Block 2}
-
-\subsection{Block 3}
-
-\subsection{Block 4}
 

### 2024-10-21 draft.tex
reformatted, ready for final proof read

@@
     T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+\renewcommand{\thesubsection}{\thesection.\alph{subsection}}
 \begin{document}
@@
     idustry suffered nearly \$1,000,000,000 in loses due to tool theft in
-    2023 alone [1], strongly indicating the need for a robust and effective 
-    theft mitigation system. We propose the BareTag Tool-Tracker, a novel
+    2016 alone [1], strongly indicating the need for a robust and effective 
+    theft mitigation system. We propose the BareTag Tool Tracker, a novel
     approach to tool tracking that utilizes Ultra-Wideband(UWB) and Bluetooth 
@@
 
-\begin{IEEEkeywords}
-component, formatting, style, styling, insert
-\end{IEEEkeywords}
-
 \section{Introduction}
-On constructions sites tools are constantly being misplaced or passed 
-around causing workers to spend extra time searching and waiting before 
+On constructions sites tools are constantly being misplaced causing workers to spend extra time searching and waiting before 
 returning to their assignments. Furthermore, in recent years research has 
@@
 companies and slowing down projects, very detrimental for small companies. 
-In recent years many different approaches have been taken to solve this 
+Many different approaches have been taken to solve this 
 growing issue.
@@
 Theft on the site is not only costly to the business owners but also 
-even more inconvenient for the construction workers and their managers. 
+inconvenient for the construction workers and their managers. 
 Due to the lack of proper tools construction workers may not continue with
@@
 result of this costs the business not just in extra wages, but also 
-extra insurance and the company’s reputation [2].
+extra insurance and reputation [2].
 
@@
 we have examined use various technology for tracking such as: AI image 
-processing, GPS, Bluetooth, and Ultra-wideband.
+processing, GPS, Bluetooth, and Ultra-Wideband.
 
@@
 \subsection{Tag}\label{AA}
-The Tag refers to the trackable device that will be attached to the tools on a worksite.
-The goal is for the Tags to be less than 31.9mm2, which is of a similar size to the Apple Airtag.
-The thickness of the Tags is aimed to be under 16mm, with the primary contributor to this size being the pouch cell 290mAh Lithium Polymer battery.
-The peak current draw of the Tag is 45mA and is out of the range that a coin cell could support, which led to the decision to use a LiPo that fits within our area size goals at 25 mm x 28mm.
-We are aiming for a one year battery life.
-The primary part of the Tag is the Qorvo DWM3001C.
-This module is driven by the nRF52833 MCU, and includes BLE, UWB, and accelerometer functionality.
-The DWM3001 provides UWB functionality and has an integrated PCB antenna which requires a keep-out zone in the Tag.
-BLE is provided by the nRF52833.
-This MCU is built on an ARM Cortex M4 and operates in the 2.4GHz band.
-This MCU is programmable over JTAG and thus requires a JTAG interface to be added to the Tag PCBs.
-The accelerometer is the LIS12DH, and is used to wake up the module upon motion detection.
-The module will set the interrupt pin on the DWM3001 high when there is motion detected.
-Otherwise, the Tag is in a low power mode to save battery life and is not receiving UWB pings.
-Therefore, before the tag goes to sleep the location needs to be checked to determine the resting location.
-The Tag has the BLE radio turned off until it exits the UWB perimeter, at which point an interrupt pin turns it on to integrate into the Apple Find My network.
-At this point, the UWB module turns off to conserve power.
-The accelerometer still regulates the power mode of the Tag depending on motion to conserve power.
-This device draws a lot of concepts from ECE 523 and ECE 304, both of which have a heavy focus on minimizing power consumption via software and component selection.
-The TPS79933 voltage regulator has an output of 3.3V when the input voltage is over 3.475V.
-This component is used in both the Tags and Anchors as both devices operate on a 3.7V input battery with 3.3V ideal operating voltage.
+The Tag refers to the trackable device that will be attached to the tools 
+on a worksite. The goal is for the Tags to be less than 31.9mm2, which is 
+of a similar size to the Apple Airtag. The thickness of the Tags is aimed 
+to be under 16mm, with the primary contributor to this size being the 
+pouch cell 290mAh Lithium Polymer battery. The peak current draw of the 
+Tag is 45mA and is out of the range that a coin cell could support, 
+which led to the decision to use a LiPo that fits within our area size 
+goals at 25 mm x 28mm. We are aiming for a one year battery life.
+The primary part of the Tag is the Qorvo DWM3001C. This module is driven 
+by the nRF52833 MCU, and includes BLE, UWB, and accelerometer 
+functionality. The DWM3001 provides UWB functionality and has an 
+integrated PCB antenna which requires a keep-out zone in the Tag. 
+BLE is provided by the nRF52833. This MCU is built on an ARM Cortex 
+M4 and operates in the 2.4GHz band. This MCU is programmable over 
+JTAG and thus requires a JTAG interface to be added to the Tag PCBs. 
+The accelerometer is the LIS12DH, and is used to wake up the module 
+upon motion detection. The module will set the interrupt pin on the 
+DWM3001 high when there is motion detected. Otherwise, the Tag is in a 
+low power mode to save battery life and is not receiving UWB pings. 
+Therefore, before the tag goes to sleep the location needs to be checked 
+to determine the resting location. The Tag has the BLE radio turned off 
+until it exits the UWB perimeter, at which point an interrupt pin turns 
+it on to integrate into the Apple Find My network. At this point, the 
+UWB module turns off to conserve power. The accelerometer still regulates 
+the power mode of the Tag depending on motion to conserve power. This 
+device draws a lot of concepts from ECE 523 and ECE 304, both of which 
+have a heavy focus on minimizing power consumption via software and 
+component selection. The TPS79933 voltage regulator has an output of 
+3.3V when the input voltage is over 3.475V. This component is used in 
+both the Tags and Anchors as both devices operate on a 3.7V input battery 
+with 3.3V ideal operating voltage.
 
 \subsection{Anchor}
-There needs to exist at least 3 anchors for the coordinates to be transmitted to the user.
-This is performed through multilateration.
-The Anchors use the same Qorvo DWM3001C modules as on the Tags as all of the submodules have a use case here too.
-The Anchors use UWB to ping the Tag and determine its location within the area defined by the proximity of the other anchors.
-They operate on this data using the nRF52833 MCU and send it to a host device over LoRaWAN.
-The RYLR998 LoRa module in the Anchors operates within the required range for LoRaWAN of 902.3 to 914.9 MHz.
-This module communicates with the MCU via UART.
-The use of these LoRa modules means that the Host Device does not need to be exactly on the site of the construction due to the kilometers of range that LoRa supports.
-We will build the LoRaWAN protocol on top of LoRa using the nRF52833 MCU.
-The use of this MCU also means that we can take advantage of the BLE it provides and use it for a variety of functions.
-The GPS coordinates of the Anchors must be known in order to get the real-world position of the Tags.
-We can also use BLE to communicate with an anchor to alert that a Tag that is in BLE mode has been returned to the UWB-supported area.
-These features result in  more power consumption than the Tags, so a 2.2Ah Lithium Ion battery is used.
-This is possible due to less size constraints for the Anchors than of the Tag.
-The size of the Anchor is not a specification that matters, however they will be able to be mounted on posts or stuck in different site locations depending on the desired use and area to cover.
-As stated before, the TPS79933 voltage regulator outputs 3.3V, which is the ideal operating voltage for the DWM3001C, along with the LoRa module.
+There needs to exist at least 3 anchors for the coordinates to be 
+transmitted to the user. This is performed through multilateration. 
+The Anchors use the same Qorvo DWM3001C modules as on the Tags as all 
+of the submodules have a use case here too. The Anchors use UWB to ping 
+the Tag and determine its location within the area defined by the 
+proximity of the other anchors. They operate on this data using the 
+nRF52833 MCU and send it to a host device over LoRaWAN. The RYLR998 
+LoRa module in the Anchors operates within the required range for 
+LoRaWAN of 902.3 to 914.9 MHz. This module communicates with the MCU 
+via UART. The use of these LoRa modules means that the Host Device does 
+not need to be exactly on the site of the construction due to the 
+kilometers of range that LoRa supports. We will build the LoRaWAN 
+protocol on top of LoRa using the nRF52833 MCU. The use of this MCU 
+also means that we can take advantage of the BLE it provides and use 
+it for a variety of functions. The GPS coordinates of the Anchors must 
+be known in order to get the real-world position of the Tags. We can 
+also use BLE to communicate with an anchor to alert that a Tag that is 
+in BLE mode has been returned to the UWB-supported area. These features 
+result in  more power consumption than the Tags, so a 2.2Ah Lithium Ion 
+battery is used. This is possible due to less size constraints for the 
+Anchors than of the Tag. The size of the Anchor is not a specification 
+that matters, however they will be able to be mounted on posts or stuck 
+in different site locations depending on the desired use and area to cover.
+As stated before, the TPS79933 voltage regulator outputs 3.3V, which is 
+the ideal operating voltage for the DWM3001C, along with the LoRa module.
 
 \subsection{Lora Dongle}
-This device is a RYLR998 operating over a USB - UART connection with the Host Device.
-It allows for the Host Device to receive the Tag coordinate data and operate on it.
-The size of this device should account for the LoRa module plus a USB/UART converter (CP2102N).
-The size should be similar to that of a USB hub, as to not be an inconvenience to have attached to a small host device.
-As such, the dimensions should be approximately 32 x 18 x 8 mm based on a combination of the component dimensions.
-The Dongle receives power from the CP2102N over a wired USB-C connection, so there is no need for an external power supply.
+This device is a RYLR998 operating over a USB - UART connection with the 
+Host Device. It allows for the Host Device to receive the Tag coordinate 
+data and operate on it. The size of this device should account for the 
+LoRa module plus a USB/UART converter (CP2102N). The size should be similar 
+to that of a USB hub, as to not be an inconvenience to have attached to a 
+small host device. As such, the dimensions should be approximately 32 x 18 
+x 8 mm based on a combination of the component dimensions. 
+The Dongle receives power from the CP2102N over a wired USB-C connection, 
+so there is no need for an external power supply.
 
@@
 
-This device can be whatever system a supervisor desires to use as long as it can support a physical USB/Serial connection, or do so using adapters.
-The Host Device is backhauling the location data of each Tag to a database where the history of the tag locations can be mapped out to determine the daily path.
-This information is also displayed in real time on a map of the desired area.
-The Host Device is also running the macless-haystack Find My server, which acts as a means for tracking the Tags that have left the UWB area and are now using BLE to integrate with the Apple Find My network.
-The tags all have unique IDs that can be linked to tools or equipment, making it easy to parse the data and determine what items have been in what location.
-
-\subsection{Authors and Affiliations}
-\textbf{The class file is designed for, but not limited to, six authors.} A 
-minimum of one author is required for all conference articles. Author names 
-should be listed starting from left to right and then moving down to the 
-next line. This is the author sequence that will be used in future citations 
-and by indexing services. Names should not be listed in columns nor group by 
-affiliation. Please keep your affiliations as succinct as possible (for 
-example, do not differentiate among departments of the same organization).
-
-\subsection{Identify the Headings}
-Headings, or heads, are organizational devices that guide the reader through 
-your paper. There are two types: component heads and text heads.
-
-Component heads identify the different components of your paper and are not 
-topically subordinate to each other. Examples include Acknowledgments and 
-References and, for these, the correct style to use is ``Heading 5''. Use 
-``figure caption'' for your Figure captions, and ``table head'' for your 
-table title. Run-in heads, such as ``Abstract'', will require you to apply a 
-style (in this case, italic) in addition to the style provided by the drop 
-down menu to differentiate the head from the text.
-
-Text heads organize the topics on a relational, hierarchical basis. For 
-example, the paper title is the primary text head because all subsequent 
-material relates and elaborates on this one topic. If there are two or more 
-sub-topics, the next level head (uppercase Roman numerals) should be used 
-and, conversely, if there are not at least two sub-topics, then no subheads 
-should be introduced.
-
-\subsection{Figures and Tables}
-\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
-bottom of columns. Avoid placing them in the middle of columns. Large 
-figures and tables may span across both columns. Figure captions should be 
-below the figures; table heads should appear above the tables. Insert 
-figures and tables after they are cited in the text. Use the abbreviation 
-``Fig.~\ref{fig}'', even at the beginning of a sentence.
-
-\section*{Acknowledgment}
-
-The preferred spelling of the word ``acknowledgment'' in America is without 
-an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-acknowledgments in the unnumbered footnote on the first page.
-
-\section*{References}
-
-Please number citations consecutively within brackets \cite{b1}. The 
-sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
-number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
-the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
-
-Number footnotes separately in superscripts. Place the actual footnote at 
-the bottom of the column in which it was cited. Do not put footnotes in the 
-abstract or reference list. Use letters for table footnotes.
-
-Unless there are six authors or more give all authors' names; do not use 
-``et al.''. Papers that have not been published, even if they have been 
-submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
-that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
-Capitalize only the first word in a paper title, except for proper nouns and 
-element symbols.
-
-For papers published in translation journals, please give the English 
-citation first, followed by the original foreign-language citation \cite{b6}.
+This device can be whatever system a supervisor desires to use as long as 
+it can support a physical USB/Serial connection, or do so using adapters. 
+The Host Device is backhauling the location data of each Tag to a database 
+where the history of the tag locations can be mapped out to determine the 
+daily path. This information is also displayed in real time on a map of 
+the desired area. The Host Device is also running the macless-haystack 
+Find My server, which acts as a means for tracking the Tags that have 
+left the UWB area and are now using BLE to integrate with the Apple Find 
+My network. The tags all have unique IDs that can be linked to tools or 
+equipment, making it easy to parse the data and determine what items have 
+been in what location.
 
 \begin{thebibliography}{00}
-\bibitem{b1} G.
-Eason, B.
-Noble, and I.
-N.
-Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil.
-Trans.
-Roy.
-Soc.
-London, vol.
-A247, pp.
-529--551, April 1955.
-\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
-\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
-\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
-\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
-\bibitem{b6} Y.
-Yorozu, M.
-Hirano, K.
-Oka, and Y.
-Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl.
-J.
-Magn.
-Japan, vol.
-2, pp.
-740--741, August 1987 [Digests 9th Annual Conf.
-Magnetics Japan, p.
-301, 1982].
-\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
+\bibitem{b1} ``2016 equipment theft report,'' 2016. [Online]. Available: https://www.ner.net/wp-content/uploads/2017/10/Annual-Theft-Report-2016.pdf. Accessed Oct. 19, 2024.
+\bibitem{b2} ``Crime in the construction industry,'' 2013. [Online]. Available: https://www.ciob.org/sites/default/files/. Accessed Oct. 19, 2024.
+\bibitem{b3} ``An exploratory look at thefts from construction sites,'' 2019. [Online]. http://ascpro0.ascweb.org/archives/cd/2019/paper/CPRT247002019.pdf. Accessed Oct. 19, 2024.
+\bibitem{b4} ``Remote Video Monitoring,'' SirixMonitoring, Sep. 13, 2024. [Online]. Available: https://sirixmonitoring.com/remote-video-monitoring/. Accessed Oct. 04, 2024.
+\bibitem{b5} ``Pros and Cons of Construction Equipment Tracking,'' Tool Tracking Software, Aug.
+02, 2023.
+[Online].
+Available:  https://gocodes.com/equipment-tracking-pros-cons/.
+Accessed: Oct.
+04, 2024.
+\bibitem{b6} ``Airtag VS GPS tracker, what is the difference ?,'' Beepings.com, 2021. [Online]. Available:https://beepings.com/airtag-vs-tracker/. Accessed: Oct. 04, 2024.
+\bibitem{b7} ``Pozyx UWB Tags - Accurate ultra-wideband trackers,'' Pozyx.io, 2024. [Online]. Available: https://www.pozyx.io/products/hardware/. Accessed: Oct. 04. 2024.
 \end{thebibliography}
 \vspace{12pt}
-\color{red}
-IEEE conference templates contain guidance text for composing and formatting conference papers.
-Please ensure that all template text is removed from your conference paper prior to submission to the conference.
-Failure to remove the template text from your paper may result in your paper not being published.
+
+\section*{Appendix}
+\setcounter{subsection}{0}
+\subsection{Design Alternatives}
+Before settling on our current design, we considered many alternatives. 
+In order to make our user-interface have real world terrain displayed 
+while tracking our tags, we need to find the coordinate positions of our 
+anchors. In order to do this, we originally considered putting GPS modules 
+on our anchors, but decided instead on creating a mobile app that can be 
+used to find the GPS of your phone when setting up the anchors. We decided 
+on this in order to save money, as individual GPS modules range from 
+\$20-\$40. We also considered purchasing a separate MCU, LoRa, and UWB 
+module to design our anchor PCBs. We found this design too complex and 
+instead decided on the same module as we are using in the Tags. We decided 
+on this current design because we want the tags and anchors to have the 
+same technology to be able to program them with the same libraries in 
+order expedite software development. Batteries have been a prominent 
+part of our design that we have put a lot of effort into deciding on. 
+Because we want the Tags to be small enough to go inside of tools without 
+manufacturers having to add room for them, we decided on very small 
+batteries inside the tag. We also considered doing energy harvesting 
+for the anchors to increase the battery life of them, but have decided 
+on large batteries for the anchors because they are less size constrained 
+compared to the Tags. In our original plan, we were going to backhaul our 
+data to a cloud database in order for processing. After some consideration, 
+we decided on sending the data to a self-hosted database to have increased 
+control over the hardware, software, and configurations, which allows us to 
+customize our database to meet our project’s needs. Having our own 
+self-hosted database can also allow us to implement our own security 
+measures, will be less expensive, and will have greater performance 
+optimized for our specific workload.
 

### 2024-10-21 draft.tex
changes

@@
 The Tag refers to the trackable device that will be attached to the tools 
-on a worksite. The goal is for the Tags to be less than 31.9mm2, which is 
+on a worksite. The goal is for the Tags to be less than $31.9mm^2$, which is 
 of a similar size to the Apple Airtag. The thickness of the Tags is aimed 
-to be under 16mm, with the primary contributor to this size being the 
-pouch cell 290mAh Lithium Polymer battery. The peak current draw of the 
-Tag is 45mA and is out of the range that a coin cell could support, 
+to be under $16mm$, with the primary contributor to this size being the 
+pouch cell $290mAh$ Lithium Polymer battery. The peak current draw of the 
+Tag is $45mA$ and is out of the range that a coin cell could support, 
 which led to the decision to use a LiPo that fits within our area size 
-goals at 25 mm x 28mm. We are aiming for a one year battery life.
-The primary part of the Tag is the Qorvo DWM3001C. This module is driven 
-by the nRF52833 MCU, and includes BLE, UWB, and accelerometer 
-functionality. The DWM3001 provides UWB functionality and has an 
-integrated PCB antenna which requires a keep-out zone in the Tag. 
-BLE is provided by the nRF52833. This MCU is built on an ARM Cortex 
-M4 and operates in the 2.4GHz band. This MCU is programmable over 
-JTAG and thus requires a JTAG interface to be added to the Tag PCBs. 
+goals at $25 \ mm \ x \ 28\ mm$. We are aiming for a one year battery life.
+\\The primary part of the Tag is the Qorvo DWM3001C. This module is driven 
+by the nRF52833 MCU which includes BLE functioality. The DWM3001C also includes, 
+UWB and accelerometer modules. The UWB functionality is driven by the DWM3110,
+which has an integrated PCB antenna. BLE is provided by the nRF52833. This MCU is built on an ARM Cortex 
+M4 and operates at $2.4GHz$. This MCU is programmable over 
+SWD and thus requires a corresponding interface to be added to the PCBs. 
 The accelerometer is the LIS12DH, and is used to wake up the module 
 upon motion detection. The module will set the interrupt pin on the 
-DWM3001 high when there is motion detected. Otherwise, the Tag is in a 
-low power mode to save battery life and is not receiving UWB pings. 
+DWM3001C high when there is motion detected. Otherwise, the Tag is in a 
+low power mode and is not receiving UWB pings. 
 Therefore, before the tag goes to sleep the location needs to be checked 
-to determine the resting location. The Tag has the BLE radio turned off 
-until it exits the UWB perimeter, at which point an interrupt pin turns 
-it on to integrate into the Apple Find My network. At this point, the 
+to determine the last known resting location. The Tag has the BLE radio turned off 
+until it exits the UWB area, at which point an interrupt pin turns 
+it on to integrate the Tag into the Apple Find My network. At this point, the 
 UWB module turns off to conserve power. The accelerometer still regulates 
@@
 component selection. The TPS79933 voltage regulator has an output of 
-3.3V when the input voltage is over 3.475V. This component is used in 
-both the Tags and Anchors as both devices operate on a 3.7V input battery 
-with 3.3V ideal operating voltage.
+$3.3V$ when the input voltage is over $3.475V$. This component is used in 
+both the Tags and Anchors as both devices operate on a $3.7V$ battery 
+with all modules operating at a $3.3V$ ideal voltage.
 
 \subsection{Anchor}
-There needs to exist at least 3 anchors for the coordinates to be 
-transmitted to the user. This is performed through multilateration. 
+There needs to exist at least $3$ anchors for the coordinates of a Tag to be 
+transmitted to the Host Device, which are calculated through multilateration. 
 The Anchors use the same Qorvo DWM3001C modules as on the Tags as all 
@@
 the Tag and determine its location within the area defined by the 
-proximity of the other anchors. They operate on this data using the 
-nRF52833 MCU and send it to a host device over LoRaWAN. The RYLR998 
-LoRa module in the Anchors operates within the required range for 
-LoRaWAN of 902.3 to 914.9 MHz. This module communicates with the MCU 
+proximity of the other anchors. They process this data using the 
+nRF52833 MCU and send it to a host device over LoRaWAN for coordinate computation. 
+The RYLR998 LoRa module in the Anchors operates within the operating range of 
+LoRaWAN: $902.3 MHz$ to $914.9 MHz$. This module communicates with the MCU 
 via UART. The use of these LoRa modules means that the Host Device does 
-not need to be exactly on the site of the construction due to the 
+not need to be on the site of the construction due to the 
 kilometers of range that LoRa supports. We will build the LoRaWAN 
-protocol on top of LoRa using the nRF52833 MCU. The use of this MCU 
-also means that we can take advantage of the BLE it provides and use 
+protocol on top of LoRa using the nRF52833 MCUs and Host Device. The use of the nRF52833 
+means that we can take advantage of the BLE it provides and use 
 it for a variety of functions. The GPS coordinates of the Anchors must 
-be known in order to get the real-world position of the Tags. We can 
-also use BLE to communicate with an anchor to alert that a Tag that is 
-in BLE mode has been returned to the UWB-supported area. These features 
+be known in order to get the real-world position of the Tags, and we can achieve
+this through a mobile app that will communicate with the Anchors over Bluetooth. 
+This operation will occur during the setup and positioning of the Anchors. We can also
+use BLE to communicate with an Anchor to alert that a Tag in 
+BLE mode has been returned within range of the Anchors. These features 
 result in  more power consumption than the Tags, so a 2.2Ah Lithium Ion 
 battery is used. This is possible due to less size constraints for the 
-Anchors than of the Tag. The size of the Anchor is not a specification 
-that matters, however they will be able to be mounted on posts or stuck 
-in different site locations depending on the desired use and area to cover.
+Anchors than of the Tag. The Anchors are not constrained by size, and therefore we 
+do not have any strict specifications for its dimensions.
 As stated before, the TPS79933 voltage regulator outputs 3.3V, which is 
-the ideal operating voltage for the DWM3001C, along with the LoRa module.
+the ideal operating voltage for the DWM3001C and LoRa module.
 
 \subsection{Lora Dongle}
-This device is a RYLR998 operating over a USB - UART connection with the 
-Host Device. It allows for the Host Device to receive the Tag coordinate 
-data and operate on it. The size of this device should account for the 
-LoRa module plus a USB/UART converter (CP2102N). The size should be similar 
-to that of a USB hub, as to not be an inconvenience to have attached to a 
-small host device. As such, the dimensions should be approximately 32 x 18 
-x 8 mm based on a combination of the component dimensions. 
-The Dongle receives power from the CP2102N over a wired USB-C connection, 
-so there is no need for an external power supply.
+This device is a RYLR998 operating over a USB/UART connection with the 
+Host Device. The Dongle allows the Host Device to receive the Tag location data in 
+reference to each Anchor, which the Host Device will then perform the multilateration algorithm on.
+The size of this device should be similar 
+to that of a commonly used USB hub, as to not be an inconvenience to have attached to a 
+small host device. The dimensions will be approximately $32 \ mm\  x \ 18 \ mm \
+x \ 8 \ mm$ based on a combination of the Dongle component dimensions, which are the LoRa 
+module and a USB/Serial converter. 
+\\ The Dongle receives power over USB from the Host Device, which the serial converter will
+drop to $3.3V$ for the ideal operating voltage of the LoRa module.
 
@@
 This device can be whatever system a supervisor desires to use as long as 
-it can support a physical USB/Serial connection, or do so using adapters. 
-The Host Device is backhauling the location data of each Tag to a database 
-where the history of the tag locations can be mapped out to determine the 
-daily path. This information is also displayed in real time on a map of 
+it can support a USB/Serial connection, or do so using adapters. The Host Device
+performs the multilateration algorithms based on the data it receives from the LoRa Dongle.
+The calculations get backhauled to a cloud database 
+where the history of Tag locations can be mapped out to determine 
+daily paths. This information is also displayed locally on a map of 
 the desired area. The Host Device is also running the macless-haystack 
-Find My server, which acts as a means for tracking the Tags that have 
-left the UWB area and are now using BLE to integrate with the Apple Find 
-My network. The tags all have unique IDs that can be linked to tools or 
+server, which acts as a means for tracking the Tags that have 
+left the UWB area and are using BLE to integrate with the Apple Find 
+My network. The Tags all have unique IDs that can be linked to tools or 
 equipment, making it easy to parse the data and determine what items have 

### 2024-10-21 draft.tex
proof read ken's writing

--- 2024-10-21 draft.tex
@@
 
+\and 
+\IEEEauthorblockN{Jeremy Gummeson}
+\textit{Professor, ECE}\\
+\textit{Advisor}
+
 }
@@
 \section{Introduction}
-On constructions sites tools are constantly being misplaced causing workers to spend extra time searching and waiting before 
-returning to their assignments. Furthermore, in recent years research has 
-shown that theft on constructions sites has built up costs for construction 
-companies and slowing down projects, very detrimental for small companies. 
-Many different approaches have been taken to solve this 
-growing issue.
+Modern construction sites heavily rely on the usage of battery operated 
+power tools, allowing construction workers to dynamically move throughout 
+a site without the need to route cables and power lines for their 
+equipment. This allows individual workers, as well as entire 
+construction firms, to be more efficient, eliminating the need to set 
+up power infrastructure at every new site, or re-work power infrastructure 
+when a site changes. However, this flexibility and ease of use create new 
+challenges to construction site efficiency. First of all, battery-powered 
+tools are often smaller and easier to misplace compared to their corded 
+predecessors, greatly reducing a firm’s overall efficiency. Second, 
+battery-powered tools are very valuable, with many cordless power tools 
+costing \$800+, greatly increasing the incentive for thieves to steal 
+cordless tools and accessories. In order to prevent inefficiencies caused 
+by misplaced tools and to deter common tool theft, a precise and scalable 
+tracking system needs to be implemented for the construction industry. 
+With this project, we propose a system that combines functionality of 
+existing item tracking and inventory management solutions, into a highly 
+precise and scalable solution specifically tailored to the construction 
+industry. While this solution is focused on preventing tool misplacement 
+and theft, we have also designed the system to be flexible, allowing 
+users to utilize the system to track and monitor equipment, materials, 
+or even individuals.
 
@@
 which can be compromised in dynamic construction environments.
-Furthermore, our system is designed to operate in very rural construction 
-areas where satellite connectivity may be limited. Unlike GPS, which 
-requires a strong satellite connection for accurate tracking, 
-ultra-wideband (UWB) technology, which our system uses, does not rely on 
-satellites, making it more reliable in such environments.
 
-A common solution and a more reliable approach is using the Apple AirTags.
-In the Apple AirTags, there are BLE modules that help it communicate 
-with other iPhones to create the Find My network. Additionally, it has 
-UWB modules that allow the user to get a more accurate location of where 
-the tag is once the AirTag is close enough to the user’s iPhone [6]. This 
+Another popular solution is the Apple AirTag.
+The Apple AirTag, uses Bluetooth Low Energy (BLE) advertisements to connect
+with devices in the Find My network (iPhone, iPads, and Macbooks). 
+Additionally, it uses UWB to allow users to get a more accurate location of where 
+the tag is once the AirTag is close enough to the owner's iPhone [6]. This 
 creates a well-rounded system to let users get a general idea of where 
-their items are with a battery life of up to a year. The difference 
+their items are with a battery life of up to one year. The difference 
 between the BareTag and the AirTag is that the BareTag is used for 
@@
 can easily find their tools, along with an additional BLE module for 
-the Find My Network feature outside of the set perimeter. Unlike Airtag, 
+the Find My network features outside of the set perimeter. Unlike Airtag, 
 our system aims to not only track and retrieve items but also to accurately 
@@
 
-The final solution takes a similar approach to BareTag. Pozyx tracks 
-items indoors by installing UWB anchors throughout the building, which 
-communicate with UWB tags. These anchors are height-adjustable and 
+The final solution, Pozyx, is most similar to the BareTag. Pozyx tracks 
+items indoors by installing UWB Anchors throughout the building, which 
+communicate with UWB Tags. These anchors are height-adjustable and 
 plugged into walls. Once configured and registered in the system, 
@@
 In locations like construction sites, where power availability may be 
-limited, anchor placement becomes a significant challenge. Additionally, 
-even though Pozyx’s UWB tags are advertised to have a battery life of over 
-five years, they are bulky and lack a low-power option. In contrast, 
-BareTag’s anchors come with pre-installed communication systems and 
-built-in batteries, making the system more portable and scalable. 
-Furthermore, BareTag’s tags feature a built-in accelerometer with an 
+limited, anchor placement becomes a significant challenge. In contrast, 
+BareTag’s Anchors are battery powered and easy to reconfigure, 
+making the system more portable and scalable. 
+Furthermore, BareTag’s Tags feature a built-in accelerometer with an 
 automatic sleep function to maximize power efficiency. This not only 
 extends battery life but also reduces the frequency of battery 
-replacements, saving time and resources. In summary, BareTag's anchors 
-do not rely on external power sources, and the tags are equipped with a 
-low-power solution, making them more suitable for outdoor and construction 
-site use compared to Pozyx’s solution.
+replacements, saving time and resources. In summary, BareTag's Anchors 
+do not rely on external power sources, and the Tags are equipped with a 
+low-power solution, making them more suitable for outdoor construction 
+site use compared to Pozyx.
 
@@
 while tracking our tags, we need to find the coordinate positions of our 
-anchors. In order to do this, we originally considered putting GPS modules 
-on our anchors, but decided instead on creating a mobile app that can be 
-used to find the GPS of your phone when setting up the anchors. We decided 
-on this in order to save money, as individual GPS modules range from 
-\$20-\$40. We also considered purchasing a separate MCU, LoRa, and UWB 
-module to design our anchor PCBs. We found this design too complex and 
-instead decided on the same module as we are using in the Tags. We decided 
-on this current design because we want the tags and anchors to have the 
-same technology to be able to program them with the same libraries in 
-order expedite software development. Batteries have been a prominent 
-part of our design that we have put a lot of effort into deciding on. 
-Because we want the Tags to be small enough to go inside of tools without 
-manufacturers having to add room for them, we decided on very small 
-batteries inside the tag. We also considered doing energy harvesting 
-for the anchors to increase the battery life of them, but have decided 
-on large batteries for the anchors because they are less size constrained 
-compared to the Tags. In our original plan, we were going to backhaul our 
-data to a cloud database in order for processing. After some consideration, 
-we decided on sending the data to a self-hosted database to have increased 
-control over the hardware, software, and configurations, which allows us to 
-customize our database to meet our project’s needs. Having our own 
-self-hosted database can also allow us to implement our own security 
-measures, will be less expensive, and will have greater performance 
-optimized for our specific workload.
+anchors. In order to do this, we originally considered putting GPS 
+modules on our anchors, but decided instead on creating a mobile app 
+that can be used to find the GPS of your phone when setting up the 
+anchors. We decided on this in order to save money, as individual GPS 
+modules range from $20-$40. We also considered purchasing a separate 
+MCU, LoRa, and UWB module to design our anchor PCBs. We found this 
+design too complex and instead decided on the same module as we are 
+using in the Tags. We decided on this current design because we want 
+the tags and anchors to have the same technology to be able to program 
+them with the same libraries in order expedite software development. 
+Batteries have been a prominent part of our design that we have put a 
+lot of effort into deciding on. Because we want the Tags to be small 
+enough to go inside of tools without manufacturers having to add room 
+for them, we decided on very small batteries inside the tag. We also 
+considered doing energy harvesting for the anchors to increase the 
+battery life of them, but have decided on large batteries for the 
+anchors because they are less size constrained compared to the Tags. 
+In our original plan, we were going to backhaul our data to a 
+self-hosted database in order for processing. After some consideration, 
+we decided that sending the data to a cloud database, such as AWS, 
+would be more beneficial for our project. Using a cloud server will 
+allow for scalability, decrease in cost, higher reliability, and 
+greater performance than a database we could host in-house. The cloud 
+database will also be easier for us to use because they come with 
+pre-existing features that will help us easily integrate our project with.
 

### 2024-10-21 draft.tex
changed anchor to Anchor

@@
 Additionally, it uses UWB to allow users to get a more accurate location of where 
-the tag is once the AirTag is close enough to the owner's iPhone [6]. This 
+the Tag is once the AirTag is close enough to the owner's iPhone [6]. This 
 creates a well-rounded system to let users get a general idea of where 
@@
 can easily find their tools, along with an additional BLE module for 
-the Find My network features outside of the set perimeter. Unlike Airtag, 
+the Find My network features outside of the set perimeter. Unlike AirTag, 
 our system aims to not only track and retrieve items but also to accurately 
@@
 items indoors by installing UWB Anchors throughout the building, which 
-communicate with UWB Tags. These anchors are height-adjustable and 
+communicate with UWB Tags. These Anchors are height-adjustable and 
 plugged into walls. Once configured and registered in the system, 
@@
 In locations like construction sites, where power availability may be 
-limited, anchor placement becomes a significant challenge. In contrast, 
+limited, Anchor placement becomes a significant challenge. In contrast, 
 BareTag’s Anchors are battery powered and easy to reconfigure, 
@@
 on a worksite. The goal is for the Tags to be less than $31.9mm^2$, which is 
-of a similar size to the Apple Airtag. The thickness of the Tags is aimed 
+of a similar size to the Apple AirTag. The thickness of the Tags is aimed 
 to be under $16mm$, with the primary contributor to this size being the 
@@
 low power mode and is not receiving UWB pings. 
-Therefore, before the tag goes to sleep the location needs to be checked 
+Therefore, before the Tag goes to sleep the location needs to be checked 
 to determine the last known resting location. The Tag has the BLE radio turned off 
@@
 have a heavy focus on minimizing power consumption via software and 
-component selection. The TPS79933 voltage regulator has an output of 
-$3.3V$ when the input voltage is over $3.475V$. This component is used in 
+component selection. The TPS79933 volTage regulator has an output of 
+$3.3V$ when the input volTage is over $3.475V$. This component is used in 
 both the Tags and Anchors as both devices operate on a $3.7V$ battery 
-with all modules operating at a $3.3V$ ideal voltage.
+with all modules operating at a $3.3V$ ideal volTage.
 
 \subsection{Anchor}
-There needs to exist at least $3$ anchors for the coordinates of a Tag to be 
+There needs to exist at least $3$ Anchors for the coordinates of a Tag to be 
 transmitted to the Host Device, which are calculated through multilateration. 
@@
 the Tag and determine its location within the area defined by the 
-proximity of the other anchors. They process this data using the 
+proximity of the other Anchors. They process this data using the 
 nRF52833 MCU and send it to a host device over LoRaWAN for coordinate computation. 
@@
 protocol on top of LoRa using the nRF52833 MCUs and Host Device. The use of the nRF52833 
-means that we can take advantage of the BLE it provides and use 
+means that we can take advanTage of the BLE it provides and use 
 it for a variety of functions. The GPS coordinates of the Anchors must 
@@
 do not have any strict specifications for its dimensions.
-As stated before, the TPS79933 voltage regulator outputs 3.3V, which is 
-the ideal operating voltage for the DWM3001C and LoRa module.
+As stated before, the TPS79933 volTage regulator outputs 3.3V, which is 
+the ideal operating volTage for the DWM3001C and LoRa module.
 
@@
 \\ The Dongle receives power over USB from the Host Device, which the serial converter will
-drop to $3.3V$ for the ideal operating voltage of the LoRa module.
+drop to $3.3V$ for the ideal operating volTage of the LoRa module.
 
@@
 04, 2024.
-\bibitem{b6} ``Airtag VS GPS tracker, what is the difference ?,'' Beepings.com, 2021. [Online]. Available:https://beepings.com/airtag-vs-tracker/. Accessed: Oct. 04, 2024.
+\bibitem{b6} ``AirTag VS GPS tracker, what is the difference ?,'' Beepings.com, 2021. [Online]. Available:https://beepings.com/airTag-vs-tracker/. Accessed: Oct. 04, 2024.
 \bibitem{b7} ``Pozyx UWB Tags - Accurate ultra-wideband trackers,'' Pozyx.io, 2024. [Online]. Available: https://www.pozyx.io/products/hardware/. Accessed: Oct. 04. 2024.
@@
 In order to make our user-interface have real world terrain displayed 
-while tracking our tags, we need to find the coordinate positions of our 
-anchors. In order to do this, we originally considered putting GPS 
-modules on our anchors, but decided instead on creating a mobile app 
+while tracking our Tags, we need to find the coordinate positions of our 
+Anchors. In order to do this, we originally considered putting GPS 
+modules on our Anchors, but decided instead on creating a mobile app 
 that can be used to find the GPS of your phone when setting up the 
-anchors. We decided on this in order to save money, as individual GPS 
-modules range from $20-$40. We also considered purchasing a separate 
-MCU, LoRa, and UWB module to design our anchor PCBs. We found this 
+Anchors. We decided on this in order to save money, as individual GPS 
+modules range from \$20-\$40. We also considered purchasing a separate 
+MCU, LoRa, and UWB module to design our Anchor PCBs. We found this 
 design too complex and instead decided on the same module as we are 
 using in the Tags. We decided on this current design because we want 
-the tags and anchors to have the same technology to be able to program 
+the Tags and Anchors to have the same technology to be able to program 
 them with the same libraries in order expedite software development. 
@@
 enough to go inside of tools without manufacturers having to add room 
-for them, we decided on very small batteries inside the tag. We also 
-considered doing energy harvesting for the anchors to increase the 
+for them, we decided on very small batteries inside the Tag. We also 
+considered doing energy harvesting for the Anchors to increase the 
 battery life of them, but have decided on large batteries for the 
-anchors because they are less size constrained compared to the Tags. 
+Anchors because they are less size constrained compared to the Tags. 
 In our original plan, we were going to backhaul our data to a 
@@
 greater performance than a database we could host in-house. The cloud 
-database will also be easier for us to use because they come with 
-pre-existing features that will help us easily integrate our project with.
+database will also be easier for us to use because it comes with 
+pre-existing features that will make project integration easier.
 

### 2024-12-19 PDR/PDR_draft_of_SDP_report/draft.tex
fic

--- 2024-10-21 draft.tex
@@
     base station runs the aggregated distance data through a multilateration
-    algorithm that can calculate the Tag's location with $\pm$ 10 cm accuracy.
+    algorithm that can calculate the Tag's location with 50 cm accuracy.
     The calculated location is then output to a local terminal, as well as 
     uploaded to a cloud database for future reference. Altogether, the BareTag Tool-Tracker
-    is highly accurate ($\pm$ 10 cm), low-power (1 year of battery life), and
+    is highly accurate (50 cm), low-power (1 year of battery life), and
     scalable (increase range by adding additional Anchors).
@@
     \hline
-    Should easily be scalable to increase the range of the UWB perimeter 
-    by adding more Anchors at desired locations.
+    Able to increase range of the UWB perimeter by adding more Anchors.
     &
@@
     when adding a new Anchor.\\
+    \hline
+    Create a user-friendly GUI that displays geographical locations of multiple Tags.
+    &
+    Have a non-team member use our application and easily track Tags spread around a zone.\\
     \hline
@@
 been in what location. 
+\subsection{3D Localization}
+To find the z-coordinate of the Tag using only three Anchors, 
+we need the distances between the Anchors and the distances between 
+the Tag and Anchors. The shape the Anchors and Tag form is known as a 
+tetrahedral. Using the volume and the base area of the tetrahedral we 
+are able to find the height which represents the Tag’s z-coordinate. 
+In [8] we know that using Heron’s formula on the distances between the 
+Anchors we can get the area of the base
+\[S_{ABC} = \sqrt{(p - AB)\cdot(p-AC)\cdot(p-BC)}\]
+and using Euler’s formula we can get the volume of the tetrahedral.
+\[V_{HABC}^2 = \frac{1}{36}
+\begin{vmatrix}
+    a^2 & \frac{a^2+b^2-n^2}{2} & \frac{a^2+c^2-m^2}{2} \\
+    \frac{a^2+b^2-n^2}{2} & b^2 & \frac{b^2+c^2-l^2}{2} \\
+    \frac{a^2+c^2-m^2}{2} & \frac{b^2+c^2-l^2}{2} & c^2
+\end{vmatrix}\]
+
+By rearranging the formula for finding the volume of a pyramid
+\[V_{HABC} = \frac{1}{3}S_{ABC} \cdot H\]
+
+we get the height of the tetrahedral as a function of volume and base.
+\[H = 3 \cdot \frac{V_{HABC}}{S_{ABC}}\]
+Then, using the volume and area that we previously calculated, 
+we get the height of the tetrahedral, which is also the z-coordinate of
+the Tag. To validate that this method works we ran a simulation through 
+Blender and confirmed that the equations do indeed give us the correct 
+z-coordinate.
+
+\section{THE PROTOTYPE}
+\subsection{Prototype Overview}
+The prototype currently consists of 3 hardware components, each with 
+associated software to control their functionality. The 3 hardware 
+components are the Tag, the Anchor, and a LoRa dongle connected to the 
+host computer.
+The Tag consists of a DWM3001C UWB, BLE, and IMU combo module, along with 
+associated programming headers, debug LEDs, and a 290 mAh LiPo battery. 
+The DWM3001C allows us to use one module as our MCU and host device for 
+all radios and other peripherals required for our design. The DWM3001C 
+along with associated passive components are mounted on a custom SMT PCB 
+to make the Tag. 
+The Anchor also consists of a DWM3001C, as well as a RYLR998 LoRa radio, 
+along with a programming header, debug LEDs, and a 2200 mAh LiIon battery. 
+The RYLR998 is a hobbyist LoRa radio that allows us to transmit 256 byte 
+packets wirelessly from our Anchors to the host computer. These packets 
+communicate measured distance between Anchor and Tag, as well as data about 
+the current state of the Anchor. Same as the Tag, the DWM3001C and RYLR998 
+along with associated passive components are housed on a custom SMT PCB to 
+make the Anchor. Anchors are mounted on metal poles that allow for fast 
+reconfiguration and ease of testing indoors and outdoors. 
+The LoRa dongle connected to the host computer is a generic USB TTL to 
+UART converter connected to a RYLR998. The host computer runs a custom 
+Python script that gathers distance data from all 3 Anchors to perform a 
+trilateration algorithm to pinpoint the Tag’s current location. Anchors 
+run a custom firmware that has them send a UWB ping to the Tag around once 
+every second. A randomized delay is put between pings in order to prevent 
+two different Anchors from pinging the Tag at that same time. Once receiving 
+a distance measurement from the Tag, each Anchor relays this information to 
+the host computer using the RYLR998, controlling the module over UART. The 
+Tags run a simple custom firmware, responding to UWB pings whenever one is 
+received. Combining these hardware and software components we get a complete 
+prototype that can find a Tag’s location in real time with 50 cm accuracy.
+
+\subsection{List of Hardware and Software}
+Hardware:
+\begin{itemize}
+    \item Qorvo DWM3001C
+    \item Reyax RYLR998
+    \item 3.7V 290mAh LiPo
+    \item 3.7 2200mAh LiIon
+    \item USB-A to UART Converter
+    \item Raspberry Pi 4B
+    \item Tag-Connect Edge-Connect Programmer
+    \item SEGGER JLink Edu Mini
+\end{itemize}
+
+Software:
+\begin{itemize}
+    \item Docker
+    \item Xcode
+    \item Serial Monitor
+    \item Debian Linux
+\end{itemize}
+
+\subsection{Custom Hardware}
+We designed two custom PCBs to act as the Tag and Anchors of our system. 
+In our current system, we were able to trilaterally locate the custom PCB 
+Tag with 3 Anchors: two Qorvo DWM3001CDK development boards and one of our 
+custom PCB Anchors. Our main goal when creating our Tag PCB was to make it 
+as small as possible. We eventually want these Tags to be placeable inside 
+of tools. In our first revision, we were able to minimize the size of the Tag 
+to approximately 26.8 by 31.6 mm squared. We were also able to successfully 
+program our DWM3001C with the Edge-Connect seen in Fig 5 attached to the 
+castellated edges of our Tag PCB. Because of this, we will be able to remove 
+the 10-pin programming header seein in Fig. 3 to reduce the size of the Tag 
+PCB in our second revision.
+
+While the Tag and Anchor PCBs look quite different, they are populated with 
+very similar components. The major difference between the two is the LoRa 
+module that can be seen extending off the left side of the Anchor PCB in Fig. 
+4. The LoRa module on the Anchor is used to communicate distance  measurements 
+from the Anchors to a base station in order to perform our trilateration 
+algorithm and locate the Tag.
+
+While we were able to integrate our PCBs to make a functioning system, we 
+still had some issues that we plan to address in our next revisions. The 
+battery connectors into the PCBs on the Tags and the Anchors are facing 
+into other components on the board, making it difficult to connect and 
+disconnect our batteries to them. Our LEDs were meant to flash during 
+transmission and reception of Ultra-Wideband pings on the Anchor and the 
+Tag. While this was not achieved, the main functionality of our PCBs were 
+not impacted. The UWB antenna on the Anchor PCB is on the opposite side of 
+the LoRa antenna because we were originally worried about signals interfering 
+with each other from the two different modules. In our next revision, we will 
+have both antennas facing up to have them in their ideal orientation for 
+transmitting and receiving signals. With this modification, we will be able to 
+maximize the area where we can precisely locate our Tag with Ultra-Wideband 
+pings. As you can see in Fig. 3 and Fig. 4, there are many more components on 
+each of our boards. These include resistors to limit current flow into certain 
+components, capacitors to reduce noise from input voltage, and LEDs that were 
+meant to be used to help us debug our system. Most importantly, we had a 
+voltage regulator to limit the input voltage into our Qorvo module to its 
+preferred 3.3 volts. We also have many test points that helped us debug our 
+system which we will remove in future revisions. Overall, our first revisions 
+of our custom PCBs worked well enough for our prototype to function properly.
 

### 2024-12-19 PDR/PDR_draft_of_SDP_report/draft.tex
mdr report update

@@
 to approximately 26.8 by 31.6 mm squared. We were also able to successfully 
-program our DWM3001C with the Edge-Connect seen in Fig 5 attached to the 
+program our DWM3001C with the Edge-Connect seen in Fig. 4 attached to the 
 castellated edges of our Tag PCB. Because of this, we will be able to remove 
-the 10-pin programming header seein in Fig. 3 to reduce the size of the Tag 
+the 10-pin programming header seein in Fig. 2 to reduce the size of the Tag 
 PCB in our second revision.
@@
 maximize the area where we can precisely locate our Tag with Ultra-Wideband 
-pings. As you can see in Fig. 3 and Fig. 4, there are many more components on 
+pings. As you can see in Fig. 2 and Fig. 3, there are many more components on 
 each of our boards. These include resistors to limit current flow into certain 
@@
 of our custom PCBs worked well enough for our prototype to function properly.
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=3]{mdr_tag_picture.png}
+\caption{Populated Tag PCB}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=3]{mdr_anchor_picture.png}
+\caption{Populated Anchor PCB}
+\end{center}
+\end{figure}
+
+\subsection{Prototype Functionality}
+In accordance with our hardware block diagrams in Fig 2, the PCBs all work 
+as intended. The modules and batteries communicate as per design. Fig. 4 
+depicts the Edge-Connect programmer pins pressed to the edge of the Tag PCB. 
+This method of programming proved to work, and we were successfully able to 
+flash firmware to the nRF52833.
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=1]{mdr_edge_connect.png}
+\caption{Edge-Connect Programmer on Tag castellated edges}
+\end{center}
+\end{figure}
+
+\subsection{Prototype Performance}
+Our Prototype met all of our proposed MDR deliverables. We were able to 
+integrate our two custom PCBs into our proposed system to track one custom 
+Tag. Although the LEDs on our PCBs did not function properly, they did not 
+cause any performance issues. Looking back at our complete design 
+specifications, our current Prototype is well on its way to achieve them. 
+For starters, we were able to track a Tag with 50 cm accuracy within a 
+predefined 10 x 10 m zone. Although this is much smaller than our system’s 
+final goal, we believe that we could have had a larger range if we had the 
+space to do so. Our system was also capable of tracking a Tag outside the 
+UWB zone using the Apple Find My network. A major performance metric that 
+we evaluated is the battery life of our system. As previously stated, our 
+design goal is to have an available system for ~1 year without the need for 
+replacing any batteries. To test our current system’s battery life, we 
+analyzed the current draw of our devices when the system was operating. 
+Fig. 5 shows the power consumption of our singular Tag PCB while it is 
+only transmitting Bluetooth Low Energy signals. For the majority of the 
+time, the Tag is idle, but it wakes up and sends a bluetooth signal 
+approximately every 5 seconds. In BLE mode, our Tag consumed 60.73 
+microamps, giving it an approximate battery life of 200 days with a 
+290 mAh battery attached to it. This was the expected power consumption 
+for our Tag in BLE mode. While our Prototype’s battery life performed well 
+in BLE mode, it did not perform close to how we want it to when sending 
+Ultra-Wideband pings. In Fig. 6, the power consumption of the Tag in UWB 
+mode can be seen changing as it switches from waiting to receive UWB pings 
+to sending them. Our Tag in UWB mode has an average current draw of 51.63 
+mA. With the 290 mAh battery our current system has attached to a Tag, its 
+battery life is under 6 hours. This battery life is well below our system’s 
+desired battery life, but there are many software power optimizations possible
+for our system.
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=1]{mdr_ble_power_consumption.png}
+\caption{Power consumption of Tag in BLE mode}
+\end{center}
+\end{figure}
+
+Lastly, we analyzed the power consumption of one of our Anchors. 
+Similarly to the Tag, our custom PCB Anchor had an average current 
+consumption of 49.23 mA. The Anchor acts as the main transmitter of the 
+signals while the Tag is the main receiver. Although our Anchor has a 
+similar current draw, it has a much longer battery life because our 
+current Anchor has a 2200 mAh battery attached to it. We are less worried 
+with the current draw of our Anchors because they are not size constrained, 
+allowing us to connect many batteries to them.
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.45]{mdr_uwb_tag_power_consumption.png}
+\caption{Power consumption of Tag in UWB Mode}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.45]{mdr_uwb_anchor_power_consumption.png}
+\caption{Power consumption of Anchor in UWB Mode}
+\end{center}
+\end{figure}
+
+\section{CONCLUSION}
+As of now, the project operates in the following states:
+\begin{itemize}
+    \item Full programming control over Tag and Anchor rev.1 PCBs
+    \item Tag lasts 4775.23 hours in BLE mode
+    \item Tag lasts 5.62 hours in UWB mode
+    \item Anchor lasts 44.7 hours
+    \item Anchors send Tag location over LoRa to host device
+    \item Find My server runs on Raspberry Pi
+\end{itemize}
+
+\section*{ACKNOWLEDGMENTS}
+We thank our advisor Professor Jeremy Gummesson for the endless 
+advice and support throughout the design process. We also thank 
+our evaluators Professor Tilman Wolf and Professor David McLaughlin 
+for essential feedback from each quarterly presentation. Of course, 
+thank you to all of the course coordinators for ensuring that the 
+necessary support has been available. Additionally, thank you to 
+Baird Soules and M5 staff for supplying a productive engineering 
+environment for prototyping and rework, and for many important 
+components that we used in our project.
 
@@
 
+\subsection{Technical Standards}
+Bluetooth Low Energy, specified by IEEE 802.15.1, is used for our Tags to 
+communicate with nearby Apple Find My ‘finder’ devices to send data to the 
+Apple Find My network for global location tracking.
+
+Ultra-Wideband is used by our Tags and Anchors for local location tracking 
+with 50cm accuracy. Our application of UWB is specified in IEEE P802.15.14, 
+which describes UWB used for Ad Hoc precision tracking. This spec builds on 
+other specs of importance such as IEEE 802.15.4.
+
+LoRa, discussed in IEEE spec P1451.5.5 , is used for sending data to the 
+Base Device. We have chosen to not implement LoRaWAN due to the features of 
+our transceiver modules, the minimal amount data we are sending, and a desire 
+to not use additional hardware such as a LoRaWAN gateway.
+
+Our chosen RF emitters all adhere to FCC guidelines as defined in FCC 47 
+CFR Part 15, which states that any radiator must be licensed unless it
+meets 47 CFR 15, unless otherwise given specific approval by the FCC. 
+FCC certifications can be found on the product pages for all of our 
+hardware radiators.
+
+\subsection{Testing Methods}
+Apple Find My integration has been tested through validating location 
+data displayed on a locally hosted GUI provided by [9].
+
+UWB tracking has been tested with 3 Anchors and 1 Tag as of MDR. 50cm 
+accuracy has been noted. This was performed through the manual creation 
+of a coordinate system in an indoor open-field environment, and moving 
+the Tag to different positions in the grid.
+
+\subsection{Project Expenditures}
+\begin{center}
+\includegraphics[scale=0.35]{mdr_project_expenditures.png}
+\end{center}
+
+\subsection{Project Management}
+Team communication is done through text and Discord. We meet on a weekly 
+basis both with each other and Professor Gummeson. GitHub and Google Drive 
+are used as our version control platforms. Each team member has a unique 
+skill-set that makes up for what another lacks, making the team dynamic 
+optimal for a complex project. The experience of our team is evenly balanced 
+with backgrounds in hardware and software, which is reflected in the 
+designated project roles.
+
+\begin{itemize}
+    \item Sean Brown - Logistics Lead and Hardware Support
+    \item Connor McGarry - Hardware Lead
+    \item Ken Su - Budget Lead and Software Support
+    \item Walter Tebbetts - Software Lead
+\end{itemize}
+
+Varying levels of class workload makes it difficult for progress reports 
+occasionally, but we try to log our progress for team review as best as 
+possible. Each team member exercises leadership skills when another is too 
+busy with external responsibilities to work on their designated part of the 
+project for a while. Each team member understanding every aspect of the 
+project has been important in helping each other out and making up for 
+occasional slow progress. The largest hurdle we have overcome thus far is 
+that of individual motivation and understanding of a team project. Some of 
+us had not worked on a project of this scale before and therefore have 
+needed to learn how to make careful decisions that affect other team members. 
+Taking accountability in a team is another skill we are learning, as there 
+have been a number of errors made where the best solution was to admit to 
+the issue as soon as possible, and then collaborate on how to solve it.
+
+\subsection{Beyond the Classroom}
+Classes that have been essential to this project so far have been ECE523, 
+ECE325, ECE304 and ECE545. These classes relate to embedded system power 
+management and networking, both of which are integral to the design of our 
+project. We plan on having discussions with the professors of these classes 
+as we progress in our development.
+
+We have had to do more detailed data sheet analysis than what we did in 
+ECE304, and Digikey has been an essential resource for component sourcing 
+and information retrieval.
+
+We have used a variety of unfamiliar software and hardware in the project, 
+all of which have required detailed research and experimentation. Since we 
+have taken inspiration from GtHub projects, we have also spent a lot of time 
+analyzing unfamiliar code to make sure we understand what we are using, and 
+ensuring we are able to edit it according to our desired optimizations.
+
 \end{document}

### 2025-02-01 Firmware/DWM3001C-starter-firmware/Src/example_selection.h
moved project build off of Docker, and simplified files

@@ -1,91 +1,0 @@
-/*! ----------------------------------------------------------------------------
- * @file    example_selection.h
- * @brief   Example selection is configured here
- *
- * @attention
- *
- * Copyright 2013 - 2021(c) Decawave Ltd, Dublin, Ireland.
- *
- * All rights reserved.
- *
- */
-
-#ifndef TEST_SELECTION_
-#define TEST_SELECTION_
-
-// #define TEST_READING_DEV_ID
-//#define TEST_SIMPLE_TX
-//#define TEST_SIMPLE_TX_PDOA
-//#define TEST_TX_SLEEP
-//#define TEST_TX_SLEEP_IDLE_RC
-//#define TEST_TX_SLEEP_AUTO
-//#define TEST_TX_SLEEP_TIMED
-//#define TEST_TX_WITH_CCA
-
-//#define TEST_SIMPLE_RX
-//#define TEST_SIMPLE_RX_NLOS
-//#define TEST_RX_DIAG
-//#define TEST_RX_SNIFF
-//#define TEST_DOUBLE_BUFFER_RX
-//#define TEST_RX_TRIM
-//#define TEST_SIMPLE_RX_PDOA
-
-//#define TEST_SIMPLE_TX_STS_SDC
-//#define TEST_SIMPLE_RX_STS_SDC
-
-//#define TEST_SIMPLE_TX_AES
-//#define TEST_SIMPLE_RX_AES
-
-//#define TEST_TX_WAIT_RESP
-//#define TEST_TX_WAIT_RESP_INT
-//#define TEST_RX_SEND_RESP
-
-//#define TEST_CONTINUOUS_WAVE
-//#define TEST_CONTINUOUS_FRAME
-
-//#define TEST_DS_TWR_INITIATOR_STS
-//#define TEST_DS_TWR_RESPONDER_STS
-
-//#define TEST_DS_TWR_INITIATOR
-//#define TEST_DS_TWR_RESPONDER
-
-//#define TEST_DS_TWR_STS_SDC_INITIATOR
-//#define TEST_DS_TWR_STS_SDC_RESPONDER
-
-//#define TEST_SS_TWR_INITIATOR
-// #define TEST_SS_TWR_RESPONDER // The code we are using for out Tags
-
-//#define TEST_SS_TWR_INITIATOR_STS
-//#define TEST_SS_TWR_RESPONDER_STS
-
[…]

### 2025-02-01 Firmware/DWM3001C-starter-firmware/Src/examples/ex_06a_ss_twr_initiator/ss_twr_initiator.c

@@ -1,297 +1,0 @@
-/*! ----------------------------------------------------------------------------
- *  @file    ss_twr_initiator.c
- *  @brief   Single-sided two-way ranging (SS TWR) initiator example code
- *
- *           This is a simple code example which acts as the initiator in a SS TWR distance measurement exchange. This application sends a "poll"
- *           frame (recording the TX time-stamp of the poll), after which it waits for a "response" message from the "DS TWR responder" example
- *           code (companion to this application) to complete the exchange. The response message contains the remote responder's time-stamps of poll
- *           RX, and response TX. With this data and the local time-stamps, (of poll TX and response RX), this example application works out a value
- *           for the time-of-flight over-the-air and, thus, the estimated distance between the two devices, which it writes to the LCD.
- *
- * @attention
- *
- * Copyright 2015 - 2021 (c) Decawave Ltd, Dublin, Ireland.
- *
- * All rights reserved.
- *
- * @author Decawave
- */
-
-#include "deca_probe_interface.h"
-#include <config_options.h>
-#include <deca_device_api.h>
-#include <deca_spi.h>
-#include <example_selection.h>
-#include <port.h>
-#include <shared_defines.h>
-#include <shared_functions.h>
-
-#if defined(TEST_SS_TWR_INITIATOR)
-
-extern void test_run_info(unsigned char *data);
-
-/* Example application name */
-#define APP_NAME "SS TWR INIT v1.0"
-
-/* Default communication configuration. We use default non-STS DW mode. */
-static dwt_config_t config = {
-    5,                /* Channel number. */
-    DWT_PLEN_128,     /* Preamble length. Used in TX only. */
-    DWT_PAC8,         /* Preamble acquisition chunk size. Used in RX only. */
-    9,                /* TX preamble code. Used in TX only. */
-    9,                /* RX preamble code. Used in RX only. */
-    1,                /* 0 to use standard 8 symbol SFD, 1 to use non-standard 8 symbol, 2 for non-standard 16 symbol SFD and 3 for 4z 8 symbol SDF type */
-    DWT_BR_6M8,       /* Data rate. */
-    DWT_PHRMODE_STD,  /* PHY header mode. */
-    DWT_PHRRATE_STD,  /* PHY header rate. */
[…]

### 2025-02-01 Firmware/DWM3001C-starter-firmware/Src/examples/ex_21_uart_test/uart_example.c

@@ -1,96 +1,0 @@
-#include "app_uart.h"
-#include "nrf_delay.h"
-#include "deca_probe_interface.h"
-#include <deca_device_api.h>
-#include <deca_spi.h>
-#include <example_selection.h>
-#include <port.h>
-#include <stdlib.h>
-
-#if defined(UART_TEST)
-
-extern void test_run_info(unsigned char *data);
-
-#define APP_NAME   "UART        V1.0"
-#define INIT_ERROR "UART INIT ERROR"
-#define TX_DELAY   500
-#define NUM_DELAYS 8
-
-#define UART_TXPIN 19 // P0.19 on DWM3001
-#define UART_RXPIN 15 // P0.15 on DWM3001
-
-// Set UART flow control to false, not needed for a single user (our case)
-static const app_uart_flow_control_t flow_control = APP_UART_FLOW_CONTROL_DISABLED;
-
-// unsigned int delays[] = {100, 200, 300, 400, 500, 600, 700, 800};
-// unsigned int cur_delay = 0;
-// unsigned int cal_delay;
-uint8_t rand_delay;
-char tx_str[20];
-
-static app_uart_comm_params_t config = {
-    .rx_pin_no = UART_RXPIN,                       // Use pin 19 as RX pin
-    .tx_pin_no = UART_TXPIN,                       // Use pin 15 as TX pin
-    .rts_pin_no = 21,                              // Random pin -- RTS not used
-    .cts_pin_no = 20,                              // Random pin -- CTS not used
-    .flow_control = flow_control,                  // Flow control disabled -- ignores RTS and CTS pins
-    .use_parity = 0,                               // Parity bit set to false
-    .baud_rate = UART_BAUDRATE_BAUDRATE_Baud115200 // Baud rate set to 115200
-};
-
-
-void uart_event_handler(app_uart_evt_t * p_event){
-    // Handle the UART event (Do nothing.)
-    return;
-}
-
-/** @brief Function for putting an entire String over UART TX
- *
- * @param str -- pointer to String to be transmitted
- * @param len -- length of the String to be transmitted
- *
- * @note May want to remove the nrf_delay_us() at the end - currently just ensures data is clear
-*/
-void uart_put_string(const char *str){
-    while(*str){
-        while(app_uart_put(*str) != NRF_SUCCESS){
-            nrf_delay_us(100);
-        }
-        str++;
-        nrf_delay_us(500);
-    }
-    nrf_delay_ms(2);
-    return;
[…]

### 2025-02-01 Firmware/Src/example_selection.h

@@ -1,0 +1,22 @@
+/*! ----------------------------------------------------------------------------
+ * @file    example_selection.h
+ * @brief   Example selection is configured here
+ *
+ * @attention
+ *
+ * Copyright 2013 - 2021(c) Decawave Ltd, Dublin, Ireland.
+ *
+ * All rights reserved.
+ *
+ */
+
+#ifndef TEST_SELECTION_
+#define TEST_SELECTION_
+
+//#define TEST_SS_TWR_RESPONDER // The code we are using for our Tags
+
+#define UART_TEST // Put random numbers out over UART
+
+// #define TWR_UART_TEST // The file for anchors
+
+#endif

### 2025-02-01 Firmware/Src/examples/ex_ss_twr_responder/ss_twr_responder.c

@@ -1,0 +1,305 @@
+/*! ----------------------------------------------------------------------------
+ *  @file    ss_twr_responder.c
+ *  @brief   Single-sided two-way ranging (SS TWR) responder example code
+ *
+ *           This is a simple code example which acts as the responder in a SS TWR distance measurement exchange. This application waits for a "poll"
+ *           message (recording the RX time-stamp of the poll) expected from the "SS TWR initiator" example code (companion to this application), and
+ *           then sends a "response" message to complete the exchange. The response message contains all the time-stamps recorded by this application,
+ *           including the calculated/predicted TX time-stamp for the response message itself. The companion "SS TWR initiator" example application
+ *           works out the time-of-flight over-the-air and, thus, the estimated distance between the two devices.
+ *
+ * @attention
+ *
+ * Copyright 2015 - 2021 (c) Decawave Ltd, Dublin, Ireland.
+ *
+ * All rights reserved.
+ *
+ * @author Decawave
+ */
+#include "deca_probe_interface.h"
+#include <deca_device_api.h>
+#include <deca_spi.h>
+#include <example_selection.h>
+#include <port.h>
+#include <shared_defines.h>
+#include <shared_functions.h>
+
+#if defined(TEST_SS_TWR_RESPONDER)
+
+extern void test_run_info(unsigned char *data);
+
+/* Example application name */
+#define APP_NAME "SS TWR RESP v1.0"
+
+/* Default communication configuration. We use default non-STS DW mode. */
+static dwt_config_t config = {
+    5,                /* Channel number. */
+    DWT_PLEN_128,     /* Preamble length. Used in TX only. */
+    DWT_PAC8,         /* Preamble acquisition chunk size. Used in RX only. */
+    9,                /* TX preamble code. Used in TX only. */
+    9,                /* RX preamble code. Used in RX only. */
+    1,                /* 0 to use standard 8 symbol SFD, 1 to use non-standard 8 symbol, 2 for non-standard 16 symbol SFD and 3 for 4z 8 symbol SDF type */
+    DWT_BR_6M8,       /* Data rate. */
+    DWT_PHRMODE_STD,  /* PHY header mode. */
+    DWT_PHRRATE_STD,  /* PHY header rate. */
[…]

### 2025-02-01 PDR/PDR_draft_of_SDP_report/draft.tex
idk, connor did PCB stuff

@@
 have a heavy focus on minimizing power consumption via software and 
-component selection. The TPS79933 volTage regulator has an output of 
-$3.3V$ when the input volTage is over $3.475V$. This component is used in 
+component selection. The TPS79933 voltage regulator has an output of 
+$3.3V$ when the input voltage is over $3.475V$. This component is used in 
 both the Tags and Anchors as both devices operate on a $3.7V$ battery 
-with all modules operating at a $3.3V$ ideal volTage.
+with all modules operating at a $3.3V$ ideal voltage.
 
@@
 do not have any strict specifications for its dimensions.
-As stated before, the TPS79933 volTage regulator outputs 3.3V, which is 
-the ideal operating volTage for the DWM3001C and LoRa module.
+As stated before, the TPS79933 voltage regulator outputs 3.3V, which is 
+the ideal operating voltage for the DWM3001C and LoRa module.
 
@@
 \\ The Dongle receives power over USB from the Host Device, which the serial converter will
-drop to $3.3V$ for the ideal operating volTage of the LoRa module.
+drop to $3.3V$ for the ideal operating voltage of the LoRa module.
 

### 2025-02-01 haystack/endpoint/config.py
mac

@@ -1,77 +1,0 @@
-import logging
-import os
-import configparser
-
-
-CONFIG_PATH = "data"
-CONFIG_FILE = "auth.json"
-CERT_FILE = "certificate.pem"  # optional
-KEY_FILE = "privkey.pem"  # optional
-
-
-def getConfigPath():
-    script_path = os.path.abspath(__file__)
-    return CONFIG_PATH if os.path.isabs(CONFIG_PATH) else os.path.dirname(script_path) + '/' + CONFIG_PATH
-
-
-config = configparser.ConfigParser()
-config.read(getConfigPath() + '/config.ini')
-
-
-def getAnisetteServer():
-    value = config.get('Settings', 'anisette_url')
-    if not value:
-        return 'http://anisette:6969'
-    return value
-
-
-def getPort():
-    value = config.get('Settings', 'port')
-    if not value:
-        return '6176'
-    return int(value)
-
-
-def getBindingAddress():
-    value = config.get('Settings', 'binding_address')
-    if not value:
-        return '0.0.0.0'
-    return value
-
-
-def getUser():
-    return config.get('Settings', 'appleid', fallback=None)
-
-
-def getPass():
-    return config.get('Settings', 'appleid_pass', fallback=None)
-
-
-def getConfigFile():
-    return getConfigPath() + '/' + CONFIG_FILE
-
-
-def getCertFile():
-    return getConfigPath() + '/' + config.get('Settings', 'cert', fallback=CERT_FILE)
-
-
-def getKeyFile():
-    return getConfigPath() + '/' + config.get('Settings', 'priv_key', fallback=KEY_FILE)
-
-
-def getEndpointUser():
-    return config.get('Settings', 'endpoint_user', fallback=None)
-
-
-def getEndpointPass():
-    return config.get('Settings', 'endpoint_pass', fallback=None)
-
-
-def getLogLevel():
-    logLevel = config.get('Settings', 'loglevel', fallback='INFO')
-    return logging.getLevelName(logLevel)
-
-logging.basicConfig(level=getLogLevel(),
-                    format='%(asctime)s - %(levelname)s - %(message)s')
-# Suppress http-log
-logging.getLogger('urllib3').setLevel(logging.INFO)

### 2025-02-01 haystack/endpoint/mh_endpoint.py

@@ -1,192 +1,0 @@
-#!/usr/bin/env python3
-
-import json
-import ssl
-import sys
-import os
-import requests
-from datetime import datetime
-import time
-import config
-from http.client import HTTPConnection
-import base64
-from collections import OrderedDict
-
-from http.server import BaseHTTPRequestHandler, HTTPServer
-
-from register import apple_cryptography, pypush_gsa_icloud
-
-import logging
-logger = logging.getLogger()
-
-
-class ServerHandler(BaseHTTPRequestHandler):
-
-    def addCORSHeaders(self):
-        self.send_header('Access-Control-Allow-Origin', '*')
-        self.send_header('Access-Control-Allow-Methods', 'GET, OPTIONS')
-        self.send_header("Access-Control-Allow-Headers", "X-Requested-With")
-        self.send_header("Access-Control-Allow-Headers", "Content-Type")
-        self.send_header("Access-Control-Allow-Headers", "Authorization")
-        self.send_header("Access-Control-Allow-Private-Network","true")
-
-    def authenticate(self):
-        user = config.getEndpointUser()
-        passw = config.getEndpointPass()
-        if (user is None or user == "") and (passw is None or passw == ""):
-            return True
-
-        auth_header = self.headers.get('authorization')
-        if auth_header:
-            auth_type, auth_encoded = auth_header.split(None, 1)
-            if auth_type.lower() == 'basic':
-                auth_decoded = base64.b64decode(auth_encoded).decode('utf-8')
-                username, password = auth_decoded.split(':', 1)
-                if username == user and password == passw:
-                    return True
-
-        return False
-
-    def do_OPTIONS(self):
-        self.send_response(200, "ok")
-        self.addCORSHeaders()
-        self.end_headers()
-
-    def do_GET(self):
-        if not self.authenticate():
-            self.send_response(401)
-            self.addCORSHeaders()
-            self.send_header('WWW-Authenticate', 'Basic realm="Auth Realm"')
-            self.end_headers()
-            return
-        self.send_response(200)
-        self.addCORSHeaders()
-        self.send_header('Content-type', 'text/plain')
-        self.end_headers()
-        self.wfile.write(b"Nothing to see here")
-
-    def do_POST(self):
-        if not self.authenticate():
-            self.send_response(401)
-            self.addCORSHeaders()
-            self.send_header('WWW-Authenticate', 'Basic realm="Auth Realm"')
-            self.end_headers()
-            return
[…]

### 2025-02-01 haystack/endpoint/register/apple_cryptography.py

@@ -1,77 +1,0 @@
-#!/usr/bin/env python
-
-import os
-import glob
-import datetime
-import argparse
-import base64
-import json
-import hashlib
-import codecs
-import struct
-import requests
-from cryptography.hazmat.primitives.ciphers import Cipher, algorithms, modes
-from cryptography.hazmat.primitives.asymmetric import ec
-from cryptography.hazmat.backends import default_backend
-import sqlite3
-import sys
-from .pypush_gsa_icloud import icloud_login_mobileme, generate_anisette_headers
-
-import config
-import logging
-logger = logging.getLogger()
-
-
-def sha256(data):
-    digest = hashlib.new("sha256")
-    digest.update(data)
-    return digest.digest()
-
-
-def decrypt(enc_data, algorithm_dkey, mode):
-    decryptor = Cipher(algorithm_dkey, mode, default_backend()).decryptor()
-    return decryptor.update(enc_data) + decryptor.finalize()
-
-
-def decode_tag(data):
-    latitude = struct.unpack(">i", data[0:4])[0] / 10000000.0
-    longitude = struct.unpack(">i", data[4:8])[0] / 10000000.0
-    confidence = int.from_bytes(data[8:9])
-    status = int.from_bytes(data[9:10])
-    return {'lat': latitude, 'lon': longitude, 'conf': confidence, 'status': status}
-
-
-def getAuth(regenerate=False):
-    if os.path.exists(config.getConfigFile()) and not regenerate:
-        with open(config.getConfigFile(), "r") as f:
-            j = json.load(f)
-    else:
-        logger.info('Trying to login')
-        mobileme = icloud_login_mobileme(
-            username=config.getUser(), password=config.getPass())
-
-        logger.debug('Answer from icloud login')
-        logger.debug(mobileme)
-        status = mobileme['delegates']['com.apple.mobileme']['status']
-        if status == 0:
-            j = {'dsid': mobileme['dsid'], 'searchPartyToken': mobileme['delegates']
-                 ['com.apple.mobileme']['service-data']['tokens']['searchPartyToken']}
-            with open(config.getConfigFile(), "w") as f:
-                json.dump(j, f)
-        else:
-            msg = mobileme['delegates']['com.apple.mobileme']['status-message']
-            logger.error('Invalid status: ' + str(status))
-            logger.error('Error message: ' + msg)
-            if 'blocking' in msg:
-                logger.error(
[…]

### 2025-02-01 haystack/endpoint/register/pypush_gsa_icloud.py

@@ -1,277 +1,0 @@
-import urllib3
-from getpass import getpass
-import plistlib as plist
-import json
-import uuid
-import pbkdf2
-import requests
-import hashlib
-import hmac
-import base64
-import locale
-import logging
-from datetime import datetime
-import srp._pysrp as srp
-from cryptography.hazmat.primitives import padding
-from cryptography.hazmat.primitives.ciphers import Cipher, algorithms, modes
-from Crypto.Hash import SHA256
-import config
-
-# Created here so that it is consistent
-USER_ID = uuid.uuid4()
-DEVICE_ID = uuid.uuid4()
-
-# Configure SRP library for compatibility with Apple's implementation
-srp.rfc5054_enable()
-srp.no_username_in_x()
-
-# Disable SSL Warning
-urllib3.disable_warnings()
-
-
-logger = logging.getLogger()
-
-
-def icloud_login_mobileme(username='', password=''):
-    if not username:
-        username = input('Apple ID: ')
-    if not password:
-        password = getpass('Password: ')
-    g = gsa_authenticate(username, password)
-    pet = g["t"]["com.apple.gs.idms.pet"]["token"]
-    adsid = g["adsid"]
-
-    data = {
-        "apple-id": username,
-        "delegates": {"com.apple.mobileme": {}},
-        "password": pet,
-        "client-id": str(USER_ID),
-    }
-    data = plist.dumps(data)
-    headers = {
-        "X-Apple-ADSID": adsid,
-        "User-Agent": "com.apple.iCloudHelper/282 CFNetwork/1408.0.4 Darwin/22.5.0",
-        "X-Mme-Client-Info": '<MacBookPro18,3> <Mac OS X;13.4.1;22F8> <com.apple.AOSKit/282 (com.apple.accountsd/113)>'
-    }
-    headers.update(generate_anisette_headers())
-
-    logger.info("Registering device after login")
-    resp = requests.post(
-        "https://setup.icloud.com/setup/iosbuddy/loginDelegates",
-        auth=(username, pet),
-        data=data,
-        headers=headers,
-        verify=False,
-    )
-    response = f"HTTP-Code: {resp.status_code}\n{resp.text}"
-    logger.debug(response)
-    return plist.loads(resp.content)
-
-
-def gsa_authenticate(username, password):
-    # Password is None as we'll provide it later
-    usr = srp.User(username, bytes(), hash_alg=srp.SHA256, ng_type=srp.NG_2048)
[…]

### 2025-02-01 haystack/firmware/ESP32/src/openhaystack_main.c

@@ -1,235 +1,0 @@
-#include <stdint.h>
-#include <string.h>
-#include <stdbool.h>
-#include <stdio.h>
-
-#include "freertos/FreeRTOS.h"
-#include "freertos/task.h"
-
-#include "nvs_flash.h"
-#include "esp_partition.h"
-
-#include "esp_bt.h"
-#include "esp_gap_ble_api.h"
-#include "esp_gattc_api.h"
-#include "esp_gatt_defs.h"
-#include "esp_bt_main.h"
-#include "esp_bt_defs.h"
-#include "esp_log.h"
-#include "esp_sleep.h"
-#include "esp_random.h"
-
-/* Delay between advertisement. Advertisment will only be transmitted for a short period of time (20ms) and the device will go to sleep.
-Higher delay = less power consumption, but more inaccurate tracking
- */
-#define DELAY_IN_S 60
-/* Define how often (long) a key will be reused after switching to the next one
-This is for using less keys after all. The interval for one key is (DELAY_IN_S * REUSE_CYCLES => 60s * 30 cycles = changes key every 30 min)
-Smaller number of cycles = key changes more often, but more keys needed.
- */
-#define REUSE_CYCLES 30
-
-static const char *LOG_TAG = "macless_haystack";
-
-/** Callback function for BT events */
-static void esp_gap_cb(esp_gap_ble_cb_event_t event, esp_ble_gap_cb_param_t *param);
-
-/** Random device address */
-static esp_bd_addr_t rnd_addr = {0xFF, 0xBB, 0xCC, 0xDD, 0xEE, 0xFF};
-
-/** Advertisement payload */
-static uint8_t adv_data[31] = {
-    0x1e,       /* Length (30) */
-    0xff,       /* Manufacturer Specific Data (type 0xff) */
-    0x4c, 0x00, /* Company ID (Apple) */
-    0x12, 0x19, /* Offline Finding type and length */
-    0x00,       /* State */
-    0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00,
-    0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00,
-    0x00, 0x00, 0x00, 0x00, 0x00, 0x00,
-    0x00, /* First two bits */
-    0x00, /* Hint (0x00) */
-};
-
[…]

### 2025-02-01 haystack/firmware/nrf5x/main.c

@@ -1,109 +1,0 @@
-#include <stdbool.h>
-#include <stdint.h>
-#include <stdlib.h>
-#include <time.h>
-#include <string.h>
-#include "ble_stack.h"
-#include "openhaystack.h"
-#include "app_timer.h"
-
-
-#define ADVERTISING_INTERVAL 5000  // advertising interval in milliseconds
-#define KEY_CHANGE_INTERVAL_MINUTES 30  // how often to rotate to new key in minutes
-#define MAX_KEYS 20  // maximum number of keys to rotate through
-#define KEY_CHANGE_INTERVAL_MS (KEY_CHANGE_INTERVAL_MINUTES * 60 * 1000)
-
-#define APP_TIMER_PRESCALER 0
-#define APP_TIMER_MAX_TIMERS 1 
-#define TIMER_TICKS APP_TIMER_TICKS(KEY_CHANGE_INTERVAL_MS, APP_TIMER_PRESCALER)
-#define APP_TIMER_OP_QUEUE_SIZE 4 
-
-int last_filled_index = -1;
-int current_index = 0;
-
-APP_TIMER_DEF(m_key_change_timer_id);
-
-// Create space for MAX_KEYS public keys
-static char public_key[MAX_KEYS][28] = { 
-    "OFFLINEFINDINGPUBLICKEYHERE!",
-};
-
-void setAndAdvertiseNextKey()
-{
-    // Variable to hold the data to advertise
-    uint8_t *ble_address;
-    uint8_t *raw_data;
-    uint8_t data_len;
-
-    // Disable advertising
-    sd_ble_gap_adv_stop();
-    sd_ble_gap_adv_data_set(NULL, 0, NULL, 0);
-
-    // Update key index for next advertisement...Back to zero if out of range
-    current_index = (current_index + 1) % (last_filled_index + 1); 
-    
-    // Set key to be advertised
-    data_len = setAdvertisementKey(public_key[current_index], &ble_address, &raw_data);
-
-    // Set bluetooth address
-    setMacAddress(ble_address);
-
-    // Set advertisement data
-    setAdvertisementData(raw_data, data_len);
-
-    // Start advertising
-    startAdvertisement(ADVERTISING_INTERVAL);
-}
-
-void key_change_timeout_handler(void *p_context)
-{
-    setAndAdvertiseNextKey();
-}
-
-static void timer_config(void)
-{
-    uint32_t err_code;
-
[…]

### 2025-02-01 haystack/firmware/nrf5x/openhaystack.c

@@ -1,91 +1,0 @@
-#include <stdbool.h>
-#include <stdint.h>
-#include <stdlib.h>
-#include <string.h>
-#include "openhaystack.h"
-#include <stdio.h>
-
-static uint8_t addr[6] = {0xFF, 0xBB, 0xCC, 0xDD, 0xEE, 0xFF};
-
-static uint8_t offline_finding_adv_template[] = {
-	0x1e,		/* Length (30) */
-	0x00,		/* Airtag is 0xFF Iphone is 0x00 so stalke alerts should not be senr */
-	0x4c, 0x00, /* Company ID (Apple) */
-	0x12, 0x19, /* Offline Finding type and length */
-	0x00,		/* State */
-	0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00,
-	0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00,
-	0x00, 0x00, 0x00, 0x00, 0x00, 0x00,
-	0x00, /* First two bits */
-	0x00, /* Hint (0x00) */
-};
-
-/*
- * set_addr_from_key will set the bluetooth address from the first 6 bytes of the key used to be advertised
- */
-void set_addr_from_key(const char *key)
-{
-	/* copy first 6 bytes */
-	addr[5] = key[0] | 0b11000000;
-	addr[4] = key[1];
-	addr[3] = key[2];
-	addr[2] = key[3];
-	addr[1] = key[4];
-	addr[0] = key[5];
-}
-
-/*
- * fill_adv_template_from_key will set the advertising data based on the remaining bytes from the advertised key
- */
-void fill_adv_template_from_key(const char *key)
-{
-
-	size_t key_size = 28;
-	char key_hex[28 * 5 + 1];
-
-	// Ausgabe des key-Arrays als Hexadezimalwerte
-	for (size_t i = 0; i < key_size; i++)
-	{
-		snprintf(&key_hex[i * 5], 6, "0x%02X,", (unsigned char)key[i]);
-	}
-
-	memcpy(&offline_finding_adv_template[7], &key[6], 22);
-	/* append two bits of public key */
-
-	size_t offline_finding_adv_template_size = sizeof(offline_finding_adv_template);
-
-	// Erstellen eines String-Puffers, der groß genug ist, um das Array aufzunehmen
-	char string_buffer[offline_finding_adv_template_size * 5 + 1]; // Jeder Wert benötigt bis zu 4 Zeichen und ein Nullterminator
-
[…]

### 2025-02-01 haystack/firmware/openhaystack-firmware/apps/openhaystack-alternative/aliexpress_board.h

@@ -1,89 +1,0 @@
-/* Copyright (c) 2016 Nordic Semiconductor. All Rights Reserved.
- *
- * The information contained herein is property of Nordic Semiconductor ASA.
- * Terms and conditions of usage are described in detail in NORDIC
- * SEMICONDUCTOR STANDARD SOFTWARE LICENSE AGREEMENT.
- *
- * Licensees are granted free, non-transferable use of the information. NO
- * WARRANTY of ANY KIND is provided. This heading must NOT be removed from
- * the file.
- *
- */
-#ifndef ALIEXPRESS_BOARD_H
-#define ALIEXPRESS_BOARD_H
-
-#ifdef __cplusplus
-extern "C" {
-#endif
-
-// LEDs definitions
-#define LEDS_NUMBER    1
-
-#define LED_1          29
-
-#define LEDS_ACTIVE_STATE 0
-
-#define LEDS_LIST { LED_1}
-
-#define BSP_LED_0      LED_1
-
-#define LEDS_INV_MASK  0
-
-#define BUTTONS_NUMBER 1
-
-#define BUTTON_START   28
-#define BUTTON_1       28
-#define BUTTON_STOP    28
-#define BUTTON_PULL    NRF_GPIO_PIN_PULLUP
-
-#define BUTTONS_ACTIVE_STATE 0
-
-#define BUTTONS_LIST { BUTTON_1 }
-
-#define BSP_BUTTON_0   BUTTON_1
-
-#define RX_PIN_NUMBER  11
-#define TX_PIN_NUMBER  12
-#define CTS_PIN_NUMBER UART_PIN_DISCONNECTED
-#define RTS_PIN_NUMBER UART_PIN_DISCONNECTED
-#define HWFC           false
-
-// Arduino board mappings
-#define ARDUINO_SCL_PIN             27    // SCL signal pin
-#define ARDUINO_SDA_PIN             26    // SDA signal pin
-#define ARDUINO_AREF_PIN            2     // Aref pin
-#define ARDUINO_13_PIN              25    // Digital pin 13
-#define ARDUINO_12_PIN              24    // Digital pin 12
-#define ARDUINO_11_PIN              23    // Digital pin 11
-#define ARDUINO_10_PIN              22    // Digital pin 10
-#define ARDUINO_9_PIN               20    // Digital pin 9
-#define ARDUINO_8_PIN               19    // Digital pin 8
-
[…]

### 2025-02-01 haystack/firmware/openhaystack-firmware/apps/openhaystack-alternative/ble_stack.c

@@ -1,85 +1,0 @@
-#include <stdbool.h>
-#include <stdint.h>
-#include <string.h>
-#include "ble_stack.h"
-
-/*******************************************************************************
- *   BLE stack specific functions
- ******************************************************************************/
-
-/*  
- *  init_ble will initialize the ble stack, it will use the crystal definition based on NRF_CLOCK_LFCLKSRC. 
- *  In devices with no external crystal you should use the internal rc. You can look at the e104bt5032a_board.h file
- */
-void init_ble() {
-    uint32_t err_code;
-    nrf_clock_lf_cfg_t clock_lf_cfg = NRF_CLOCK_LFCLKSRC;
-
-    // Initialize the SoftDevice handler module.
-    SOFTDEVICE_HANDLER_INIT(&clock_lf_cfg, NULL);
-
-    ble_enable_params_t ble_enable_params;
-    err_code = softdevice_enable_get_default_config(CENTRAL_LINK_COUNT, // central link count
-                                                    PERIPHERAL_LINK_COUNT, // peripheral link count
-                                                    &ble_enable_params);
-    ble_enable_params.common_enable_params.vs_uuid_count = BLE_UUID_VS_COUNT_MIN;
-    APP_ERROR_CHECK(err_code);
-
-    //Check the ram settings against the used number of links
-    CHECK_RAM_START_ADDR(CENTRAL_LINK_COUNT, PERIPHERAL_LINK_COUNT);
-
-    // Enable BLE stack.
-    err_code = softdevice_enable(&ble_enable_params);
-    APP_ERROR_CHECK(err_code);
-
-    // Use max power.
-    sd_ble_gap_tx_power_set(4);
-}
-
-/**
- * setMacAddress will set the bluetooth address
- */
-void setMacAddress(uint8_t *addr) {
-    ble_gap_addr_t gap_addr;
-    uint32_t err_code;
-
-    memcpy(gap_addr.addr, addr, sizeof(gap_addr.addr));
-    gap_addr.addr_type = BLE_GAP_ADDR_TYPE_PUBLIC;
-    err_code = sd_ble_gap_address_set(BLE_GAP_ADDR_CYCLE_MODE_NONE, &gap_addr);
-    APP_ERROR_CHECK(err_code);
-}
-
-/**
- * setAdvertisementData will set the data to be advertised
- */
[…]

### 2025-02-01 haystack/firmware/openhaystack-firmware/apps/openhaystack-alternative/ble_stack.h

@@ -1,40 +1,0 @@
-#include "softdevice_handler.h"
-#include "boards.h"
-#include "ble.h"
-#include "ble_gap.h"
-#include "app_error.h"
-
-#ifndef uint8_t
-    typedef __uint8_t uint8_t;
-    typedef __uint16_t uint16_t;
-    typedef __uint32_t uint32_t;
-    typedef __uint64_t uint64_t;
-#endif
-
-/*  
- *  init_ble will initialize the ble stack, it will use the crystal definition based on NRF_CLOCK_LFCLKSRC. 
- *  In devices with no external crystal you should use the internal rc. You can look at the e104bt5032a_board.h file
- */
-void init_ble();
-
-/**
- * setMacAddress will set the bluetooth address
- */
-void setMacAddress(uint8_t *addr);
-
-/**
- * setAdvertisementData will set the data to be advertised
- */
-void setAdvertisementData(uint8_t *data, uint8_t dlen);
-
-/**
- * Start advertising at the specified interval
- * 
- * @param[in] interval advertising interval in milliseconds
- */
-void startAdvertisement(int interval);
-
-/**
- * Function for the Power manager.
- */
-void power_manage(void);

### 2025-02-01 haystack/firmware/openhaystack-firmware/apps/openhaystack-alternative/e104bt5032a_board.h

@@ -1,78 +1,0 @@
-/* Copyright (c) 2016 Nordic Semiconductor. All Rights Reserved.
- *
- * The information contained herein is property of Nordic Semiconductor ASA.
- * Terms and conditions of usage are described in detail in NORDIC
- * SEMICONDUCTOR STANDARD SOFTWARE LICENSE AGREEMENT.
- *
- * Licensees are granted free, non-transferable use of the information. NO
- * WARRANTY of ANY KIND is provided. This heading must NOT be removed from
- * the file.
- *
- */
-#ifndef CUSTOM_BOARD_H
-#define CUSTOM_BOARD_H
-
-#ifdef __cplusplus
-extern "C" {
-#endif
-
-#define NRF_CLOCK_LFCLKSRC {.source        = NRF_CLOCK_LF_SRC_RC,            \
-                            .rc_ctiv       = 16,                             \
-                            .rc_temp_ctiv  = 2,                              \
-                            .xtal_accuracy = 1}
-
-// LEDs definitions
-#define LEDS_NUMBER    0
-#define LEDS_ACTIVE_STATE 0
-
-#define LEDS_LIST { }
-
-#define LEDS_INV_MASK  0
-
-#define BUTTONS_NUMBER 0
-
-#define BUTTON_PULL    NRF_GPIO_PIN_PULLDOWN
-
-#define BUTTONS_ACTIVE_STATE 0
-
-#define BUTTONS_LIST { }
-
-#define RX_PIN_NUMBER  11
-#define TX_PIN_NUMBER  12
-#define CTS_PIN_NUMBER UART_PIN_DISCONNECTED
-#define RTS_PIN_NUMBER UART_PIN_DISCONNECTED
-#define HWFC           false
-
-// Arduino board mappings
-#define ARDUINO_SCL_PIN             27    // SCL signal pin
-#define ARDUINO_SDA_PIN             26    // SDA signal pin
-#define ARDUINO_AREF_PIN            2     // Aref pin
-#define ARDUINO_13_PIN              25    // Digital pin 13
-#define ARDUINO_12_PIN              24    // Digital pin 12
-#define ARDUINO_11_PIN              23    // Digital pin 11
-#define ARDUINO_10_PIN              22    // Digital pin 10
-#define ARDUINO_9_PIN               20    // Digital pin 9
-#define ARDUINO_8_PIN               19    // Digital pin 8
-
-#define ARDUINO_7_PIN               18    // Digital pin 7
[…]

### 2025-02-01 haystack/firmware/openhaystack-firmware/apps/openhaystack-alternative/main.c

@@ -1,42 +1,0 @@
-#include <stdbool.h>
-#include <stdint.h>
-#include <string.h>
-#include "ble_stack.h"
-#include "openhaystack.h"
-
-/** 
- * advertising interval in milliseconds 
- */
-#define ADVERTISING_INTERVAL 5000
-
-static char public_key[28] = "OFFLINEFINDINGPUBLICKEYHERE!";
-
-/**
- * main function
- */
-int main(void) {
-    // Variable to hold the data to advertise
-    uint8_t *ble_address;
-    uint8_t *raw_data;
-    uint8_t data_len;
-
-    // Set key to be advertised
-    data_len = setAdvertisementKey(public_key, &ble_address, &raw_data);
-
-    // Init BLE stack
-    init_ble();
-
-    // Set bluetooth address
-    setMacAddress(ble_address);
-
-    // Set advertisement data
-    setAdvertisementData(raw_data, data_len);
-
-    // Start advertising
-    startAdvertisement(ADVERTISING_INTERVAL);
-
-    // Go to low power mode
-    while (1) {
-        power_manage();
-    }
-}

### 2025-02-01 haystack/firmware/openhaystack-firmware/apps/openhaystack-alternative/nrf_drv_config.h

@@ -1,355 +1,0 @@
-/* Copyright (c) 2015 Nordic Semiconductor. All Rights Reserved.
- *
- * The information contained herein is property of Nordic Semiconductor ASA.
- * Terms and conditions of usage are described in detail in NORDIC
- * SEMICONDUCTOR STANDARD SOFTWARE LICENSE AGREEMENT.
- *
- * Licensees are granted free, non-transferable use of the information. NO
- * WARRANTY of ANY KIND is provided. This heading must NOT be removed from
- * the file.
- *
- */
-
-#ifndef NRF_DRV_CONFIG_H
-#define NRF_DRV_CONFIG_H
-
-#define NRF_LOG_USES_RTT 0
-#define NRF_LOG_USES_UART 0
-
-/* CLOCK */
-#define CLOCK_CONFIG_XTAL_FREQ          NRF_CLOCK_XTALFREQ_Default
-#define CLOCK_CONFIG_LF_SRC             NRF_CLOCK_LF_SRC_Xtal
-#define CLOCK_CONFIG_LF_RC_CAL_INTERVAL RC_2000MS_CALIBRATION_INTERVAL
-#define CLOCK_CONFIG_IRQ_PRIORITY       APP_IRQ_PRIORITY_LOW
-
-/* GPIOTE */
-#define GPIOTE_ENABLED 1
-
-#if (GPIOTE_ENABLED == 1)
-#define GPIOTE_CONFIG_USE_SWI_EGU false
-#define GPIOTE_CONFIG_IRQ_PRIORITY APP_IRQ_PRIORITY_LOW
-#define GPIOTE_CONFIG_NUM_OF_LOW_POWER_EVENTS 1
-#endif
-
-/* TIMER */
-#define TIMER0_ENABLED 0
-
-#if (TIMER0_ENABLED == 1)
-#define TIMER0_CONFIG_FREQUENCY    NRF_TIMER_FREQ_16MHz
-#define TIMER0_CONFIG_MODE         TIMER_MODE_MODE_Timer
-#define TIMER0_CONFIG_BIT_WIDTH    TIMER_BITMODE_BITMODE_32Bit
-#define TIMER0_CONFIG_IRQ_PRIORITY APP_IRQ_PRIORITY_LOW
-
-#define TIMER0_INSTANCE_INDEX      0
[…]

### 2025-02-01 haystack/firmware/openhaystack-firmware/apps/openhaystack-alternative/openhaystack.c

@@ -1,65 +1,0 @@
-#include <stdbool.h>
-#include <stdint.h>
-#include <stdlib.h>
-#include <string.h>
-#include "openhaystack.h"
-
-static uint8_t addr[6] = { 0xFF, 0xBB, 0xCC, 0xDD, 0xEE, 0xFF };
-
-static uint8_t offline_finding_adv_template[] = {
-	0x1e, /* Length (30) */
-	0xFF, /* MAKE IT AN IPHONE*/
-	0x4c, 0x00, /* Company ID (Apple) */
-	0x12, 0x19, /* Offline Finding type and length */
-	0x00, /* State */
-	0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00,
-	0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00,
-	0x00, 0x00, 0x00, 0x00, 0x00, 0x00,
-	0x00, /* First two bits */
-	0x00, /* Hint (0x00) */
-};
-
-/*
- * set_addr_from_key will set the bluetooth address from the first 6 bytes of the key used to be advertised
- */
-void set_addr_from_key(char key[28]) {
-	/* copy first 6 bytes */
-	addr[5] = key[0] | 0b11000000;
-	addr[4] = key[1];
-	addr[3] = key[2];
-	addr[2] = key[3];
-	addr[1] = key[4];
-	addr[0] = key[5];
-}
-
-/*
- * fill_adv_template_from_key will set the advertising data based on the remaining bytes from the advertised key
- */
-void fill_adv_template_from_key(char key[28]) {
-	/* copy last 22 bytes */
-	memcpy(&offline_finding_adv_template[7], &key[6], 22);
-	/* append two bits of public key */
-	offline_finding_adv_template[29] = key[0] >> 6;
-}
-
-/*
- * setAdvertisementKey will setup the key to be advertised
- *
- * @param[in] key public key to be advertised
- * @param[out] bleAddr bluetooth address to setup
- * @param[out] data raw data to advertise
- * 
- * @returns raw data size
- */
-uint8_t setAdvertisementKey(char *key, uint8_t **bleAddr, uint8_t **data) {
-    set_addr_from_key(key);
-	fill_adv_template_from_key(key);
-
-    *bleAddr = malloc(sizeof(addr));
-    memcpy(*bleAddr, addr, sizeof(addr));
-
-    *data = malloc(sizeof(offline_finding_adv_template));
[…]

### 2025-02-01 haystack/firmware/openhaystack-firmware/apps/openhaystack-alternative/openhaystack.h

@@ -1,24 +1,0 @@
-#include <stdbool.h>
-#include <stdint.h>
-#include <string.h>
-
-/*
- * set_addr_from_key will set the bluetooth address from the first 6 bytes of the key used to be advertised
- */
-void set_addr_from_key(char key[28]);
-
-/*
- * fill_adv_template_from_key will set the advertising data based on the remaining bytes from the advertised key
- */
-void fill_adv_template_from_key(char key[28]);
-
-/*
- * setAdvertisementKey will setup the key to be advertised
- *
- * @param[in] key public key to be advertised
- * @param[out] bleAddr bluetooth address to setup
- * @param[out] data raw data to advertise
- * 
- * @returns raw data size
- */
-uint8_t setAdvertisementKey(char *key, uint8_t **bleAddr, uint8_t **data);

### 2025-02-01 haystack/firmware/openhaystack-firmware/apps/openhaystack-alternative/simple_board.h

@@ -1,78 +1,0 @@
-/* Copyright (c) 2016 Nordic Semiconductor. All Rights Reserved.
- *
- * The information contained herein is property of Nordic Semiconductor ASA.
- * Terms and conditions of usage are described in detail in NORDIC
- * SEMICONDUCTOR STANDARD SOFTWARE LICENSE AGREEMENT.
- *
- * Licensees are granted free, non-transferable use of the information. NO
- * WARRANTY of ANY KIND is provided. This heading must NOT be removed from
- * the file.
- *
- */
-#ifndef SIMPLE_BOARD_H
-#define SIMPLE_BOARD_H
-
-#ifdef __cplusplus
-extern "C" {
-#endif
-
-#define NRF_CLOCK_LFCLKSRC {.source        = NRF_CLOCK_LF_SRC_RC,            \
-                            .rc_ctiv       = 16,                             \
-                            .rc_temp_ctiv  = 2,                              \
-                            .xtal_accuracy = 1}
-
-// LEDs definitions
-#define LEDS_NUMBER    0
-#define LEDS_ACTIVE_STATE 0
-
-#define LEDS_LIST { }
-
-#define LEDS_INV_MASK  0
-
-#define BUTTONS_NUMBER 0
-
-#define BUTTON_PULL    NRF_GPIO_PIN_PULLDOWN
-
-#define BUTTONS_ACTIVE_STATE 0
-
-#define BUTTONS_LIST { }
-
-#define RX_PIN_NUMBER  11
-#define TX_PIN_NUMBER  12
-#define CTS_PIN_NUMBER UART_PIN_DISCONNECTED
-#define RTS_PIN_NUMBER UART_PIN_DISCONNECTED
-#define HWFC           false
-
-// Arduino board mappings
-#define ARDUINO_SCL_PIN             27    // SCL signal pin
-#define ARDUINO_SDA_PIN             26    // SDA signal pin
-#define ARDUINO_AREF_PIN            2     // Aref pin
-#define ARDUINO_13_PIN              25    // Digital pin 13
-#define ARDUINO_12_PIN              24    // Digital pin 12
-#define ARDUINO_11_PIN              23    // Digital pin 11
-#define ARDUINO_10_PIN              22    // Digital pin 10
-#define ARDUINO_9_PIN               20    // Digital pin 9
-#define ARDUINO_8_PIN               19    // Digital pin 8
-
-#define ARDUINO_7_PIN               18    // Digital pin 7
[…]

### 2025-02-01 haystack/firmware/openhaystack-firmware/nrf5x-base/lib/simple_ble.c

@@ -1,958 +1,0 @@
-/*
- * BLE setup functions
- */
-
-// Standard Libraries
-#include <stdint.h>
-#include <stdbool.h>
-#include <stdio.h>
-#include <string.h>
-
-// Nordic Libraries
-#include "nordic_common.h"
-#include "ble.h"
-#include "ble_db_discovery.h"
-#include "app_util.h"
-#include "app_error.h"
-#include "ble_conn_params.h"
-#include "ble_hci.h"
-#include "ble_hrs_c.h"
-#include "ble_bas_c.h"
-#include "app_util.h"
-#include "app_timer.h"
-#include "softdevice_handler.h"
-#include "nrf_sdm.h"
-
-// device firmware update code
-#ifdef ENABLE_DFU
-#include "ble_dfu.h"
-#include "bootloader_types.h"
-#include "bootloader_util.h"
-#include "bootloader.h"
-#endif
-
-// Simple BLE files
-#include "simple_ble.h"
-#include "device_info_service.h"
-
-#ifdef ENABLE_DFU
-// Defines
-#define IRQ_ENABLED               0x01
-#define MAX_NUMBER_INTERRUPTS     32
-#define BOOTLOADER_BLE_ADDR_START 0x20007F80
-#define DFU_ADV_DATA_TYPE         0x16
-#define DFU_ADV_DATA_VERS         0x01
-#endif
-
-/*******************************************************************************
- *   STATIC AND GLOBAL VARIABLES
- ******************************************************************************/
-static const simple_ble_config_t* ble_config;
-
-simple_ble_app_t app;
-ble_gap_adv_params_t m_adv_params;
-ble_gap_sec_params_t m_sec_params = {
-    SEC_PARAM_BOND,
-    SEC_PARAM_MITM,
-#if defined(SOFTDEVICE_s130) || defined(SOFTDEVICE_s132)
-    SEC_PARAM_LESC,
-    SEC_PARAM_KEYPRESS,
-#endif
-    SEC_PARAM_IO_CAPABILITIES,
-    SEC_PARAM_OOB,
-    SEC_PARAM_MIN_KEY_SIZE,
-    SEC_PARAM_MAX_KEY_SIZE,
-#if defined(SOFTDEVICE_s130) || defined(SOFTDEVICE_s132)
-    {0, 0, 0, 0},
-    {0, 0, 0, 0}
-#endif
-};
-
[…]

### 2025-02-02 Firmware/Src/examples/ex_uart_test/uart_example.c
got UART RX working

@@ -15,6 +15,7 @@ extern void test_run_info(unsigned char *data);
 #define INIT_ERROR "UART INIT ERROR"
 #define TX_DELAY   500
 #define NUM_DELAYS 8
+#define MAX_BUF_SIZE 32
 
 #define UART_TXPIN 19 // P0.19 on DWM3001
 #define UART_RXPIN 15 // P0.15 on DWM3001
@@ -22,11 +23,14 @@ extern void test_run_info(unsigned char *data);
 // Set UART flow control to false, not needed for a single user (our case)
 static const app_uart_flow_control_t flow_control = APP_UART_FLOW_CONTROL_DISABLED;
 
-// unsigned int delays[] = {100, 200, 300, 400, 500, 600, 700, 800};
-// unsigned int cur_delay = 0;
-// unsigned int cal_delay;
+char err_buf[MAX_BUF_SIZE];
+
 uint8_t rand_delay;
-char tx_str[20];
+char tx_str[MAX_BUF_SIZE];
+char rx_buf[MAX_BUF_SIZE];
+uint8_t rx_byte;
+char rx_indx = 0;
+char rx_flag = 0;
 
 static app_uart_comm_params_t config = {
     .rx_pin_no = UART_RXPIN,                       // Use pin 19 as RX pin
@@ -40,7 +44,59 @@ static app_uart_comm_params_t config = {
 
 
 void uart_event_handler(app_uart_evt_t * p_event){
-    // Handle the UART event (Do nothing.)
+    // Handle the UART event 
+    switch(p_event->evt_type){
+        case APP_UART_DATA_READY:
+            test_run_info((const char*) "APP UART DATA READY -- NO FIFO");
+            break;
+        
+        case APP_UART_FIFO_ERROR:
+            /**
+             * TODO: Connect this with the appropriate error in nrf_error.h -> use some sort of patern matching to output a string indicating the error
+             */
+            sprintf(err_buf, "APP UART FIFO ERROR: %d", p_event->data.error_code);
+            test_run_info((const char*) err_buf);
+            break;
+            
+        case APP_UART_COMMUNICATION_ERROR:
+            /**
+             * TODO: Apparently, this error is stored in nrf5x_bitfields.h, I can't find this file... 
+             */
+            sprintf(err_buf, "APP UART COMMS ERROR: %d", p_event->data.error_communication);
+            test_run_info((const char*) err_buf);
+            break;
+
+        case APP_UART_TX_EMPTY:
[…]

### 2025-02-02 Firmware/Src/examples/ex_uart_test/uart_example.c
added comments

@@ -13,8 +13,6 @@ extern void test_run_info(unsigned char *data);
 
 #define APP_NAME   "UART        V1.0"
 #define INIT_ERROR "UART INIT ERROR"
-#define TX_DELAY   500
-#define NUM_DELAYS 8
 #define MAX_BUF_SIZE 32
 
 #define UART_TXPIN 19 // P0.19 on DWM3001
@@ -42,10 +40,16 @@ static app_uart_comm_params_t config = {
     .baud_rate = UART_BAUDRATE_BAUDRATE_Baud115200 // Baud rate set to 115200
 };
 
-
+/** @brief Function to handle UART events, including: UART_RX, UART_TX complete, and UART errors 
+ * 
+ * @param p_event -- ptr to app_uart_evt_t struct -- detailed in app_uart.h file
+ * 
+ * @note has TODOs that should be addressed -- not urgent
+ */
 void uart_event_handler(app_uart_evt_t * p_event){
     // Handle the UART event 
     switch(p_event->evt_type){
+        //UART RX a byte if FIFO enabled -- FIFO not currently enabled
         case APP_UART_DATA_READY:
             test_run_info((const char*) "APP UART DATA READY -- NO FIFO");
             break;
@@ -66,10 +70,12 @@ void uart_event_handler(app_uart_evt_t * p_event){
             test_run_info((const char*) err_buf);
             break;
 
+        // When UART finished TXing a byte -- for debugging
         case APP_UART_TX_EMPTY:
             test_run_info((const char*) "UART TX EMPTY");
             break;
 
+        // UART RX a byte
         case APP_UART_DATA:
             while(app_uart_get(&rx_byte) != NRF_SUCCESS){
                 nrf_delay_us(100);
@@ -103,7 +109,6 @@ void uart_event_handler(app_uart_evt_t * p_event){
 /** @brief Function for putting an entire String over UART TX
  *
  * @param str -- pointer to String to be transmitted
- * @param len -- length of the String to be transmitted
  *
  * @note May want to remove the nrf_delay_us() at the end - currently just ensures data is clear
 */

### 2025-02-04 Firmware/Src/example_selection.h
toggle led on interrupt

@@ -15,8 +15,10 @@
 
 //#define TEST_SS_TWR_RESPONDER // The code we are using for our Tags
 
-#define UART_TEST // Put random numbers out over UART
+//#define UART_TEST // Put random numbers out over UART
 
 // #define TWR_UART_TEST // The file for anchors
+
+#define TEST_TWI_ACC
 
 #endif
